### 2023-06-16 paper/paper.tex
init

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[review]{EMNLP2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

\usepackage{microtype}
\usepackage{enumitem}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{color}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb,amsthm}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{caption}
%\usepackage{paralist}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{url}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\our}{\mbox{\textsc{SimDE}}}
% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{SimDE: Simple Contrastive Learning for Document Embeddings}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

% \author{First Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\\And
%   Second Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\}

\author{Yujie Wang \\
  Claremont Graduate University 
  \texttt{yujie.wang@cgu.edu} \\\And
  Mike Izbicki \\
  Claremont McKenna College
  \texttt{Michael.Izbicki@ClaremontMcKenna.edu} \\}

\begin{document}
\maketitle
\begin{abstract}
%High-quality text embeddings are essential to various natural language understanding tasks especially for low-resource settings. 
%Existing methods are proposed for general text understanding but representations for long text are less explored.
%Basically, to have better embeddings for long text, a model should have the ability to recognize key information in a long text. 
%We introduce the $\our$ 
%To this end, we present \our, a simple unsupervised contrastive learning framework for long text embeddings in this paper. 
%Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision. 
%The positive pairs are constructed by our key information redundancy assumption for long text.
% Experimental results on five datasets show that \our~outperforms the state-of-the-art models by $3.9\%$ on classification tasks and $12.0\%$ macro-F1 in average respectively under general and few-shot text classification settings.

% This paper presents $\our$, the first unsupervised pretraining
% method designed specifically for documents.
% $\our$ uses the contrastive learning framework, and our main contribution is a simple but effective data augmentation technique for generating similar text pairs.
%A key advantage of $\our$ over other techniques for working with
%long text is that it requires no changes to model architecture, and so it is widely applicable.
% Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision or specific model architectures, and so it is widely applicable.
%We use $\our$ pretraining to improve the embeddings of previously
%developed state-of-the-art models.
% The positive pairs are constructed by our key information redundancy assumption for documents.
% On standard classification datasets, $\our$ improves all baseline
% models, with an average improvement of $3.9\%$ macro F1 score.
% We also consider a few-shot setting where we show an average
% improvement of $12.0\%$.

Existing pretrained transformer models generate high-quality sentence and paragraph embeddings, but do not work well for large documents.
A growing body of research tackles this problem by proposing new model architectures that are more efficient with large context windows, but all of this research still uses the classic token masking strategy for training.
Token masking is a fundamentally \emph{local} operation in that context of the entire document is rarely needed to correctly predict the masked token---the words much closer to the token will have a much larger
influence.
We propose a novel \emph{global} method for training that requires a model to equally consider all portions of a document.
Our Simple Document Embedding (SimDE) method is based on contrastive learning.
Like token masking, SimDE is fully unsupervised and can work with any existing model architecture.
We experimentally evaluate the SimDE on a wide range of architectures on standard classification datasets for large documents.
We find an average improvement of $3.9\%$ macro F1 score in a standard
regime with large training datasets and a massive $12.0\%$ improvement in the macro F1 score in a few-shot setting.
\end{abstract}

\section{Introduction}

Generating high-quality text embeddings for documents is a long-standing open problem.
Most previous studies focus on either learning sentence-level representations~\cite{Hill2016LearningDR, Logeswaran2018AnEF, Gao2021SimCSESC} where training data usually contain short text or designing specific model structures for larger-range dependencies~\cite{Beltagy2020LongformerTL, Zaheer2020BigBT},
but effective and efficient document representation learning methods are less explored.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{fig/simde.pdf}
\caption{Overall framework of \our. The document is randomly divided into two exclusive subsets of sentences and the two subsets work as positive pairs for contrastive learning. Other instances in the same batch are used as negatives.
}
\label{overall}
\end{figure}

In this paper, we present the $\our$ which is the first unsupervised training method designed specifically for documents.
The training procedure of $\our$ can work with any model architecture to improve document representations. 
Specifically, $\our$ uses contrastive learning,
and our key contribution is a new method for generating positive samples for contrastive learning.
To this end, we first investigate the information redundancy with two methods (details in Appendix~\ref{app:redundacy}) on five datasets for different lengths of documents.
We find (1) information redundancy is larger as the length of the documents is increasing and (2) sentences from the same document usually contain repeated information. 
Based on this observation, we can assume that the model can still learn the semantics of documents even if we drop some sentences. Hence, as shown in Figure~\ref{overall}, we randomly divide the original documents into two parts by sentences as positive pairs. Due to redundancies, our model can still recognize the two pairs have the same semantics. 
The intuition behind this method is that we expect the model will pull representations of two subsets together in the latent space by paying more attention to common keywords so that the model can learn key information from documents automatically.

To evaluate the quality of document embeddings, we conduct standard and few-shot text classification on five long text datasets involved in News and scientific articles. 
The experimental results show that \our~with two kinds of model structures (i.e.,~BERT and Longformer) can both achieve significant improvements compared to state-of-the-art baselines.

% The recurrent connections in models like the LSTM~\cite{Hochreiter1997LongSM} and GRU~\cite{Cho2014OnTP} allow information at all locations in the document to influence the final embedding,
% but they are slow to train because the models must consider each word sequentially.
% The Transformer architecture~\cite{Vaswani2017AttentionIA} uses self-attention with no recurrent connections,
% and so can be trained much faster than recurrent models.
% This has led to the widespread use of language models like BERT~\cite{Devlin2019BERTPO} and ELMO~\cite{Peters2018DeepCW} that are pre-trained on large scale web data.
% Unfortunately, the memory requirements of self-attention scale as $O(n^2)$ and so are not suitable for long documents.
%Large scale pre-trained transformers like BERT~\cite{} and ELMO~\cite{} are currently state-of-the-art for many NLP tasks that require only short-term dependencies in text.
%These transformers do not handle long-term dependencies well, however, because they require $O(n^2)$ memory for the size of the context window.
% The LongFormer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT} models allow larger-range dependencies by introducing improved attention mechanisms that reduce the memory requirements down to $O(n)$.
% This previous research focuses on designing new model architectures suitable for long text,
% but in this paper we present the $\our$ training procedure that can work with any model architecture.
%All of this previous research focuses on designing new model architectures.
%Our paper introduces a new training method called the $\our$ that works for any model architecture.

% $\our$ is the first unsupervised training method designed specifically for long text.
% Previous methods for training on long text either require supervision~\cite{} or use the masked language modeling (MLM) technique~\cite{}.
% In MLM, we replace a token from the input text with a special ``mask'' token and train the model to predict which token was removed.
% The MLM pretraining method has been shown to work well for short-text documents~\cite{},
% but we argue that it sub-optimal for long text because most of the information for predicting the masked token is available near the token.
% The $\our$ pretraining technique is designed to force the model to learn long range dependencies within a document.
% Specifically, $\our$ uses contranstive learning,
% and our key contribution is a new method for generating the positive samples for contrastive learning (see Figure~\ref{overall} above).
%The most similar work to our own is the \texttt{SimCSE} method which uses contrastive learning to pre-train text models,

%Supervised methods cannot be used for large-scale pretraining of models, however, so we present the

Our paper is organized as follows.
In Section~\ref{sec:method} we formally define the contrastive learning problem and our novel $\our$ training method.
%We highlight how our $\our$ method improves on related contrastive learning frameworks like \texttt{SimCSE}
In Section~\ref{sec:experiments} we develop a new experimental evaluation procedure for documents.
We conclude in Section~\ref{sec:conclusion} by emphasizing that all of our models and datasets are open source.

\section{Method}

\label{sec:method}
In this section, we first formally define contrastive learning, then we describe our \our~method.
\subsection{Contrastive Learning}
Contrastive Learning aims to learn effective representations by pulling semantically close neighbors together and pushing apart non-neighbors in the latent space~\cite{Hadsell2006DimensionalityRB}.
It assumes a contrastive instance $\{x, x^{+}, x_1^{-},\dots,x_{N-1}^{-}\}$ including one positive and $N-1$ negative instances and their representations $\{\mathbf{h}, \mathbf{h}^{+}, \mathbf{h}_1^{-}, \dots,
\mathbf{h}_{N-1}^{-}\}$, where $x$ and $x^{+}$ are semantically related.
we follow the contrastive learning framework~~\cite{Chen2020ASF, Li2022UCTopicUC} and take cross-entropy as our objective function:
\begin{equation}
\label{cl}
    l = -\log \frac{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}}{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}+ \sum_{i=1}^{N-1}e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}_i^{-})/\tau}}
\end{equation}
where $\tau$ is a temperature hyperparameter and $\mathrm{sim}(\mathbf{h}_1, \mathbf{h}_2)$ is the cosine similarity $\frac{\mathbf{h}_1^{\top}\mathbf{h}_2}{\Vert \mathbf{h}_1 \Vert \cdot \Vert \mathbf{h}_2 \Vert}$.
In this work, we encode input texts using a pre-trained language model such as BERT~\cite{Devlin2019BERTPO}. Following BERT, we use the first special token \texttt{[CLS]} as the representation of the input and fine-tune all the parameters using the contrastive learning objective in Equation~\ref{cl}.

\subsection{SimDE}
The critical problem in contrastive learning is how to construct positive pairs $(x, x^{+})$.
In representation learning for visual tasks~\cite{Chen2020ASF}, an effective solution is to take two random transformations of the same image (e.g.,~flipping, rotation).
Similarly, in language representations, previous works~\cite{Gao2021SimCSESC, Karpukhin2020DensePR, Meng2021COCOLMCA, Li2022UCTopicUC} apply augmentation techniques such as dropout, word deletion, reordering, and masking.

In this paper, we propose a new method to construct positive instances for documents. 
The basic idea of positive instance construction for contrastive learning is adding random noises to the original data for augmentation. 
The augmented data should have similar representations to the original data. 
Models trained by contrastive losses on augmented data will have an increased ability to learn important features in the data.
To add random noises in documents, we find documents usually has higher information redundancy than sentences (Table~\ref{redundancy} in Appendix). 
With this observation, we can have an assumption: 
the semantics of a document will not be changed even if we drop half of the document. 
We can construct positive pairs under this assumption easily on any text dataset without supervision.
Specifically, for each document in the dataset, we randomly split sentences in the document into two subsets and the two sentence sets do not have intersections. 
In the two subsets, we keep the order of sentences in the original document to form two new documents. 
According to our assumption, the two new documents should have the same semantics and hence they are used as a positive pair in contrastive learning.

Consider an example (in Figure~\ref{overall}) to understand our positive instance construction process:
Suppose we have a document $T = (s_1, s_2,\dots,s_n)$ where $s_i$ is the $i$-th sentence in document and $n$ is the number of sentences, each sentence will be sent to anchor set or positive set with the same probability ($50\%$). 
The sentences in the same set (i.e.,~anchor or positive) will be concatenated in the same order of $T$ to form one positive pair $(T^+_1, T^+_2)$ for contrastive learning. 
Positive pairs constructed by this method will not contain the same sentence and hence prevent models from overfitting on recognizing the same sentences. 
Instead, models are guided to learn keywords appearing in positive instances so as to improve the ability to recognize key information. 
We split the document at sentence level instead of word level (e.g.,~word deletion for augmentation) because the word-level splitting will cause the discrepancy between pretraining and finetuning and then lead to performance decay.

For negative instances, we use in-batch instances following previous contrastive frameworks~\cite{Gao2021SimCSESC, Li2022UCTopicUC}.

\section{Experiments}

\label{sec:experiments}
In this section, we evaluate the effectiveness of our method by conducting text classification tasks. 
To eliminate the influence of different model structures and focus on the quality of text embeddings. 
We freeze the parameters of different text encoders and fine-tune only a multi-layer perceptron (MLP) to classify the embeddings of text encoders.
We also visualize the attention weights between baselines and \our.

\begin{table}[t]
\centering
    \input{fig/dataset}
    \caption{Statistics of datasets. Ave. and Med. stand for the average and median number of words respectively in one data instance.}
    \label{dataset}
\end{table}

\begin{table*}
    \centering
% \scalebox{0.7}{
% \setlength{\tabcolsep}{1.mm}{
    \input{fig/result.tex}
    % }}
    \caption{For all performance measures, larger numbers are better. Our pre-trained model achieves the best results in all cases.}
    \vspace{-3mm}
    \label{results}
\end{table*}

\subsection{Pretraining Details}
For pre-training, we start from the pretrained BERT-BASE model~\cite{Devlin2019BERTPO} and the Longformer~\cite{Beltagy2020LongformerTL} model~\footnote{The Longformer checkpoint is pretrained on long documents by MLM task and is available from Huggingface.} 
We follow previous works~\cite{Gao2021SimCSESC, Li2022UCTopicUC}: the masked language model (MLM) loss and the contrastive learning loss are used concurrently with in-batch negatives. 
We use English Wikipedia~\footnote{https://en.wikipedia.org/} articles as pretraining data and each article is viewed as one training instance. 
The total number of training instances is 6,218,825. 
Our pretraining learning rate is 5e-5, batch size is 36 and 12 for BERT and Longformer structure respectively. Our model is optimized by AdamW~\cite{Kingma2014AdamAM} in 1 epoch. 
The temperature $\tau$ in the contrastive loss is set to $0.05$ and the weight of MLM is set to $0.1$ following previous work~\cite{Gao2021SimCSESC}.

\subsection{Datasets}
We use the following classic documents datasets to evaluate our method:
(1) Fake News Corpus~\footnote{https://github.com/several27/FakeNewsCorpus};
(2) 20NewsGroups~\cite{Lang1995NewsWeederLT};
(3) arXiv articles dataset~\footnote{https://www.kaggle.com/datasets/Cornell-University/arxiv};
(4) New York Times Annotated Corpus (NYT) ~\cite{sandhaus2008new}; and
(5) BBCNews~\footnote{http://mlg.ucd.ie/datasets/bbc.html}.
We do not use semantic textual similarity (STS) tasks~\cite{Agirre2012SemEval2012T6} because the sentences in these tasks are short which is not suitable to evaluate long text embeddings.

\subsection{Baselines}
We compare our pre-trained model to the baselines of two groups.
(1) BERT based models include BERT~\cite{Devlin2019BERTPO}, SimCSE~\cite{Gao2021SimCSESC}, CT-BERT~\cite{Carlsson2021SemanticRW}. For a fair comparison, we also train a SimCSE with our pretraining dataset (SimCSE$_\mathrm{long}$).
(2) Transformers specified for long sequences include Longformer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT}.
We train two versions of \our~with BERT and Longformer (i.e.,~\our$_\mathrm{bert}$ and \our$_{\mathrm{long}}$) for comparison.
We do not include RoBERTa~\cite{Liu2019RoBERTaAR} and IS-BERT~\cite{Zhang2020AnUS} as our baselines because SimCSE achieves better results than these methods according to the paper.

\subsection{Text Classification}
In the standard text classification task, we classify text embeddings with the full training set. 
Training details are in Appendix~\ref{app:details}.

\textbf{Results.}
Table~\ref{results} shows the evaluation results on different datasets. 
Overall, we can see that \our~achieves the best performance over the 5 document datasets and consistently improves the document embeddings with BERT and Longformer structures. 
Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE) outperform general language representations (i.e., BERT) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings. SimCSE pretrained with our document data (i.e.,~SimCSE$_{\mathrm{long}}$) has similar results as the original SimCSE which indicates simplely increasing the length of pretraining text cannot improve document embeddings.
Compared to SimCSE and Longformer, our model achieves $3.9\%$ and $9.4\%$ average macro-F1 improvements with BERT and Longformer structures respectively. Hence, our contrastive learning method is effective for document embeddings.

\subsection{Few-shot Text Classification}
To show the performance of different text embeddings under low-resource settings, we evaluate our model with few-shot training instances.
Training details are in Appendix~\ref{app:details}.

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{fig/few_shot.pdf}
\caption{Performance of different models with different numbers of instances per class under few-shot setting.}
\label{few_shot}
\end{figure}

\textbf{Results.} 
Table~\ref{results} shows the results of few-shot text classification on these five datasets. 
We can see that \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively. These improvements are higher than standard text classification. 
Besides, we also compare the performance of different baselines and \our$_{\mathrm{bert}}$ with different numbers of training instances on 20News. 
The results in Figure~\ref{few_shot} show the improvements from our method become larger as the number of training instances decreases indicating the importance of high-quality document embeddings for low-resource settings. 
Furthermore, our method achieves the best results under different numbers of training instances.

\subsection{Document Retrieval}
We use document retrieval to evaluate the ability of learning the similarity score between two vectors \cite{ Guo2016ADR}. We follow the document retrieval experiment \cite{Tay2020LongRA} and use the ACL Anthology Network (AAN) \cite{Radev2009TheAA} dataset, which identifies if two papers have a citation link, a common setup used in long-form document matching \cite{Jiang2019SemanticTM,Yang2020Beyond5T}.

\textbf{Results.} 
\begin{table*}
    \centering
    \input{fig/document_rerival.tex}
    \caption{}
    \vspace{-3mm}
    \label{retrieval}
\end{table*}
Table~\ref{retrieval} shows the results of document retrieval experiment on AAN dataset.

\section{Conclusion}
\label{sec:conclusion}
In this work, we propose an unsupervised contrastive learning framework for long text embeddings. 
Our method provides a new method for long text data augmentation without any supervision and language models can get large-scale pretraining on any long text. 
We conduct extensive experiments on text classification tasks under fully supervised and few-shot settings.
Results show that our pre-trained model greatly outperforms state-of-the-art text embeddings, especially when the training data is limited.

\section*{Limitations}
The limitations of our method are as follows:
\begin{enumerate}[nosep,leftmargin=*]
    \item Our method requires human-annotated data, which is expensive and time-consuming.
    \item Our method focuses on document embeddings, we cannot claim the method works well for sentence embeddings.
    \item Due to computing resource limitations, the text used in our work cannot be extremely long to verify the effectiveness of our method in this case.
\end{enumerate}

\section*{Ethics Statement}
We do not anticipate any major ethical concerns; learning document embedding is a fundamental problem in natural language processing. Ethical considerations seem low-risk for the specific datasets studied here because they are all published.

%\section*{Acknowledgements}

% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\clearpage
\appendix
\section{Appendix}

\subsection{Related Work}

\textbf{Text Embeddings}. Learning text embeddings is a fundamental task in natural language processing (NLP) which can be used in information retrieval~\cite{Thakur2021BEIRAH}, text similarity~\cite{Gao2021SimCSESC}, classification~\cite{Minaee2021DeepLB}, etc. Existing works focus on learning general text embeddings for different applications. SimCSE~\cite{Gao2021SimCSESC} augment training data by Dropout~\cite{Srivastava2014DropoutAS} to construct positive data for contrastive learning. Sentence-BERT~\cite{Reimers2019SentenceBERTSE} employs siamese and triplet network structures to compare the labeled sentences in the natural language inference (NLI) dataset. Contriever~\cite{Izacard2021UnsupervisedDI} learns text embeddings for information retrieval via contrastive learning considering multilingual corpus. Instructor~\cite{Su2022OneEA} collects a massive dataset from 330 diverse NLP tasks and formulates all tasks into information retrieval tasks with prompts. 
Previous works either rely on massive manually annotated data~\cite{Su2022OneEA, Reimers2019SentenceBERTSE} or focus only on short text (i.e.,~sentences) embeddings~\cite{Gao2021SimCSESC}.
In this paper, we study unsupervised representation learning of document embeddings which usually have longer text than general sentence embeddings and this task brings new challenges for models to understand a document.

\textbf{Model Structures for Documents}. Due to the limitations of Transformer~\cite{Vaswani2017AttentionIA} on long documents, Another line of work studies the efficient model structures which can be effective to encode documents. For example, Longformer~\cite{Beltagy2020LongformerTL} introduces an attention mechanism that scales linearly with sequence length, making it easy to process long documents. BigBird~\cite{Zaheer2020BigBT} proposes a sparse attention mechanism that reduces this quadratic dependency to linear. \citet{Bulatov2022RecurrentMT} combines the memory mechanism in LSTM~\cite{Hochreiter1997LongSM} with Transformer to let transformers encode extremely long sequences. Comparing these methods which focus on designing models for long documents, our work studies the effective training method for long documents which can be adopted to any model structures for pre-training.

\subsection{Redundancy}
\label{app:redundacy}
\begin{table}[t]
    \input{fig/redundancy}
    \caption{Information redundancies for different lengths (i.e.,~word numbers) of text: (1) 0-50 (2) 51-100 (3) 101-200 (4) 201-300 (5) more than 300.}
    \label{redundancy}
\end{table}

We evaluate the redundancy of the text by two methods: (1) counting the repeated verbs and nouns in the text; (2) comparing inner-document and inter-document sentence similarities.

For (1), we first use SpaCy~\footnote{https://spacy.io/} to find verbs and nouns and get their lemmatizations. Intuitively, if the redundancy of a document is high, nouns and verbs will be repeated frequently to express the same topic. Hence, redundancies $R$ in our paper are computed as:
\begin{equation}
    R = \frac{N_{\mathrm{nouns, verbs}}}{D_{\mathrm{nouns, verbs}}}
\end{equation}
where $N_{\mathrm{nouns, verbs}}$ denotes the number of nouns and verbs in a document and $D_{\mathrm{nouns, verbs}}$ is the number of distinct nouns and verbs.

For (2), we compute sentence similarities to compare inner-document and inter-document information. Specifically, we first split documents into sentences and encode these sentences with pre-trained SimCSE~\cite{Gao2021SimCSESC}. Then, we calculate cosine similarities for every two sentences in the same documents (i.e.,~inner-document) and from different documents (i.e.,~inter-document). Results from five datasets are shown in Table~\ref{sent_sim}. We can see that sentences in the same documents have higher similarities compared to sentences from different documents. These results show that sentences in the same documents usually contain repeated information and hence have higher redundancy (i.e.,~sentences expressing similar semantics).

\label{app:sent_sim}
\begin{table}[t]
    \input{fig/sent_sim}
    \caption{Inner-document and inter-document sentences similarities measured by SimCSE.}
    \label{sent_sim}
\end{table}

\subsection{Training Details}
\label{app:details}
For text classification, the learning rate for fine-tuning is 3e-4; the batch size is 8; the maximum sequence length is 512 tokens. 
We fine-tune the last MLP layer on these five datasets and evaluate the classification performance with accuracy and macro-F1 scores.
For few-shot text classification, we sample 10 data instances per class for the FakeNewsCorpus dataset and the arXiv dataset and 5 data instances per class for the other three datasets. 
Other settings are the same as the standard text classification. 
Since there is randomness in sampling, we repeat every experiment 10 times and take the average value of metrics.

\subsection{Attention Weights}
\label{app:attention}
To explore the difference between \our~and other models, we analyze the attention weights of Transformers in different models on the NYT dataset (details in Appendix~\ref{app:attention}). The average weights of different kinds of words are shown in Figure~\ref{attentions}.  We can see that our model has more than $40\%$ higher attention weights on nouns compared to BERT and SimCSE.~\citet{martin-johnson-2015-efficient} shows nouns are more informative than other words in the document understanding. Hence, our pretraining method increases the attention weights of models on nouns which results in higher performance on long text classification.

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{fig/attentions.pdf}
\caption{Attention weights from different models on the NYT dataset.}  
\label{attentions}
\end{figure}

We compute the attention weights for Transformers as follows:
(1) we first extract the attention weights between \texttt{[CLS]} token and all the other tokens;
(2) we compute the averaged weights along different heads in multi-head attention;
(3) the attention weights of the last layer in Transformers are used as the weights for words.
Averaged values are computed for nouns, verbs, adjectives, and other words.

\end{document}

### 2023-06-16 paper/emnlp2023-latex/emnlp2023.tex
update

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[review]{EMNLP2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

\usepackage{microtype}
\usepackage{enumitem}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{color}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb,amsthm}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{caption}
%\usepackage{paralist}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{url}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\our}{\mbox{\textsc{SimLDE}}}
% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{SimLDE: Simple Contrastive Learning for Long Document Embeddings}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

% \author{First Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\\And
%   Second Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\}

\author{Yujie Wang \\
  Claremont Graduate University 
  \texttt{yujie.wang@cgu.edu} \\\And
  Mike Izbicki \\
  Claremont McKenna College
  \texttt{Michael.Izbicki@ClaremontMcKenna.edu} \\}

\begin{document}
\maketitle
\begin{abstract}
This paper presents $\our$, the first unsupervised pretraining
method designed specifically for long document.
$\our$ uses the contrastive learning framework, and our main contribution is a simple but effective data augmentation technique for generating similar text pairs.
%A key advantage of $\our$ over other techniques for working with
%long text is that it requires no changes to model architecture, and so it is widely applicable.
Specifically, we pretrain a language model to distinguish if two documents have the same topic without any supervision or specific model architectures, and so it is widely applicable.
%We use $\our$ pretraining to improve the embeddings of previously
%developed state-of-the-art models.
The positive pairs are constructed by our key information redundancy assumption for long text.
On standard classification datasets, $\our$ improves all baseline
models, with an average improvement of $3.9\%$ macro F1 score.
We also consider a few-shot setting where we show an average
improvement of $12.0\%$.
\end{abstract}

\section{Introduction}

These instructions are for authors submitting papers to EMNLP 2023 using \LaTeX. They are not self-contained. All authors must follow the general instructions for *ACL proceedings,\footnote{\url{http://acl-org.github.io/ACLPUB/formatting.html}} as well as guidelines set forth in the EMNLP 2023 call for papers. This document contains additional instructions for the \LaTeX{} style files.
The templates include the \LaTeX{} source of this document (\texttt{EMNLP2023.tex}),
the \LaTeX{} style file used to format it (\texttt{EMNLP2023.sty}),
an ACL bibliography style (\texttt{acl\_natbib.bst}),
an example bibliography (\texttt{custom.bib}),
and the bibliography for the ACL Anthology (\texttt{anthology.bib}).

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf). Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.
\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
\label{tab:accents}
\end{table}
\section{Preamble}
\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
\hline
\citep{ct1965} & \verb|\citep| & \verb|\cite| \\
\citealp{ct1965} & \verb|\citealp| & no equivalent \\
\citet{ct1965} & \verb|\citet| & \verb|\newcite| \\
\citeyearpar{ct1965} & \verb|\citeyearpar| & \verb|\shortcite| \\
\citeposs{ct1965} & \verb|\citeposs| & no equivalent \\
\citep[FFT;][]{ct1965} &  \verb|\citep[FFT;][]| & no equivalent\\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL-style files for compatibility.
}
\end{table*}
The first line of the file must be
\begin{quote}
\begin{verbatim}
\documentclass[11pt]{article}
\end{verbatim}
\end{quote}
To load the style file in the review version:
\begin{quote}
\begin{verbatim}
\usepackage[review]{EMNLP2023}
\end{verbatim}
\end{quote}
For the final version, omit the \verb|review| option:
\begin{quote}
\begin{verbatim}
\usepackage{EMNLP2023}
\end{verbatim}
\end{quote}
To use Times Roman, put the following in the preamble:
\begin{quote}
\begin{verbatim}
\usepackage{times}
\end{verbatim}
\end{quote}
(Alternatives like txfonts or newtx are also acceptable.)
Please see the \LaTeX{} source of this document for comments on other packages that may be useful.
Set the title and author using \verb|\title| and \verb|\author|. Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.
By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
\begin{quote}
\begin{verbatim}
\setlength\titlebox{<dim>}
\end{verbatim}
\end{quote}
where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.

\section{Document Body}

\subsection{Footnotes}

Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

\subsection{Tables and figures}

See Table~\ref{tab:accents} for an example of a table and its caption.
\textbf{Do not override the default caption sizes.}

\subsection{Hyperlinks}

Users of older versions of \LaTeX{} may encounter the following error during compilation: 
\begin{quote}
\tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
\end{quote}
This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.

\subsection{Citations}

Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).

\subsection{References}

\nocite{Ando2005,borschinger-johnson-2011-particle,andrew2007scalable,rasooli-tetrault-2015,goodman-etal-2016-noise,harper-2014-learning}

The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
\begin{quote}
\begin{verbatim}
\bibliographystyle{acl_natbib}
\bibliography{custom}
\end{verbatim}
\end{quote}
You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the Anthology and your own .bib file, use the following instead of the above.
\begin{quote}
\begin{verbatim}
\bibliographystyle{acl_natbib}
\bibliography{anthology,custom}
\end{verbatim}
\end{quote}
Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.

\subsection{Appendices}

Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.

\section{Bib\TeX{} Files}
\label{sec:bibtex}

Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization. The recommended way of typing special characters is shown in Table~\ref{tab:accents}.

Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.

\section*{Limitations}
EMNLP 2023 requires all submissions to have a section titled ``Limitations'', for discussing the limitations of the paper as a complement to the discussion of strengths in the main text. This section should occur after the conclusion, but before the references. It will not count towards the page limit.

The discussion of limitations is mandatory. Papers without a limitation section will be desk-rejected without review.
ARR-reviewed papers that did not include ``Limitations'' section in their prior submission, should submit a PDF with such a section together with their EMNLP 2023 submission.

While we are open to different types of limitations, just mentioning that a set of results have been shown for English only probably does not reflect what we expect. 
Mentioning that the method works mostly for languages with limited morphology, like English, is a much better alternative.
In addition, limitations such as low scalability to long text, the requirement of large GPU resources, or other things that inspire crucial further investigation are welcome.

\section*{Ethics Statement}
Scientific work published at EMNLP 2023 must comply with the \href{https://www.aclweb.org/portal/content/acl-code-ethics}{ACL Ethics Policy}. We encourage all authors to include an explicit ethics statement on the broader impact of the work, or other ethical considerations after the conclusion but before the references. The ethics statement will not count toward the page limit (8 pages for long, 4 pages for short papers).

\section*{Acknowledgements}
This document has been adapted by Yue Zhang, Ryan Cotterell and Lea Frermann from the style files used for earlier ACL and NAACL proceedings, including those for 
ACL 2020 by Steven Bethard, Ryan Cotterell and Rui Yan,
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shin Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is a section in the appendix.

\end{document}

### 2023-06-20 emnlp2023-latex/paper.tex
update

--- 2023-06-16 paper/paper.tex
@@
 % the typewriter font.
-\usepackage{inconsolata}
+% \usepackage{inconsolata}
 
@@
 \newcommand{\todo}[1]{{\color{red}{#1}}}
-\newcommand{\our}{\mbox{\textsc{SimDE}}}
+\newcommand{\our}{\mbox{\textsc{DocSplit}}}
 % If the title and author information does not fit in the area allocated, uncomment the following
@@
 
-\title{SimDE: Simple Contrastive Learning for Document Embeddings}
+\title{DocSplit: Simple Contrastive Pretraining for \\ Large Document Embeddings}
 
@@
 \begin{abstract}
-%High-quality text embeddings are essential to various natural language understanding tasks especially for low-resource settings. 
-%Existing methods are proposed for general text understanding but representations for long text are less explored.
-%Basically, to have better embeddings for long text, a model should have the ability to recognize key information in a long text. 
-%We introduce the $\our$ 
-%To this end, we present \our, a simple unsupervised contrastive learning framework for long text embeddings in this paper. 
-%Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision. 
-%The positive pairs are constructed by our key information redundancy assumption for long text.
-% Experimental results on five datasets show that \our~outperforms the state-of-the-art models by $3.9\%$ on classification tasks and $12.0\%$ macro-F1 in average respectively under general and few-shot text classification settings.
 
-% This paper presents $\our$, the first unsupervised pretraining
-% method designed specifically for documents.
-% $\our$ uses the contrastive learning framework, and our main contribution is a simple but effective data augmentation technique for generating similar text pairs.
-%A key advantage of $\our$ over other techniques for working with
-%long text is that it requires no changes to model architecture, and so it is widely applicable.
-% Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision or specific model architectures, and so it is widely applicable.
-%We use $\our$ pretraining to improve the embeddings of previously
-%developed state-of-the-art models.
-% The positive pairs are constructed by our key information redundancy assumption for documents.
-% On standard classification datasets, $\our$ improves all baseline
-% models, with an average improvement of $3.9\%$ macro F1 score.
-% We also consider a few-shot setting where we show an average
-% improvement of $12.0\%$.
-
-Existing pretrained transformer models generate high-quality sentence and paragraph embeddings, but do not work well for large documents.
-A growing body of research tackles this problem by proposing new model architectures that are more efficient with large context windows, but all of this research still uses the classic token masking strategy for training.
-Token masking is a fundamentally \emph{local} operation in that context of the entire document is rarely needed to correctly predict the masked token---the words much closer to the token will have a much larger
-influence.
-We propose a novel \emph{global} method for training that requires a model to equally consider all portions of a document.
-Our Simple Document Embedding (SimDE) method is based on contrastive learning.
-Like token masking, SimDE is fully unsupervised and can work with any existing model architecture.
-We experimentally evaluate the SimDE on a wide range of architectures on standard classification datasets for large documents.
-We find an average improvement of $3.9\%$ macro F1 score in a standard
-regime with large training datasets and a massive $12.0\%$ improvement in the macro F1 score in a few-shot setting.
+Existing model pretraining methods only consider local information.
+For example, in the popular token masking strategy, the words closer to the masked token are more important for prediction than words far away.
+This results in pretrained models that generate high-quality sentence embeddings, but low-quality embeddings for large documents.
+We propose a new pretraining method called $\our$ which forces models to consider the entire global context of a large document.
+Our method uses a contrastive loss where the positive examples are randomly sampled sections of the input document, and negative examples are randomly sampled sections of unrelated documents.
+Like previous pretraining methods, $\our$ is fully unsupervised, easy to implement, and can be used to pretrain any model
+architecture.
+Our experiments show that $\our$ outperforms other pretraining methods for document classification, few shot learning, and information retrieval tasks.
 \end{abstract}
@@
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{fig/simde.pdf}
+\includegraphics[width=\columnwidth]{fig/docsplit.pdf}
 \caption{Overall framework of \our.
@@
 
-To evaluate the quality of document embeddings, we conduct standard and few-shot text classification on five long text datasets involved in News and scientific articles. 
+To evaluate the quality of document embeddings, we conduct standard and few-shot text classification on five large document datasets involved in News and scientific articles.
+Moreover, to further validate the effectiveness of our method, we also conduct document retrieval on the AAN dataset which is designed for long document understanding evaluation.
 The experimental results show that \our~with two kinds of model structures (i.e.,~BERT and Longformer) can both achieve significant improvements compared to state-of-the-art baselines.
@@
 
-\subsection{SimDE}
+\subsection{DocSplit}
 The critical problem in contrastive learning is how to construct positive pairs $(x, x^{+})$.
@@
     % }}
-    \caption{For all performance measures, larger numbers are better. Our pre-trained model achieves the best results in all cases.}
+    \caption{For all performance measures, larger numbers are better.
+Our pre-trained model achieves the best results in all cases.
+*INSTRUCTOR~\cite{Su2022OneEA} includes 20News in their pretraining datasets which causes data leakage in our experiments, hence INSTRUCTOR results on 20News are not comparable to others.}
     \vspace{-3mm}
@@
 
-\subsection{Datasets}
+\subsection{Baselines}
+We compare our pre-trained model to the baselines of two groups.
+(1) Language models trained for general language understanding and sentence embeddings include BERT~\cite{Devlin2019BERTPO}, SimCSE~\cite{Gao2021SimCSESC}~\footnote{SimCSE can be viewed as an ablation model without document splitting.}, CT-BERT~\cite{Carlsson2021SemanticRW}, Contriever~\cite{Izacard2021UnsupervisedDI} and INSTRUCTOR~\cite{Su2022OneEA}.
+For a fair comparison, we also train a SimCSE with our pretraining dataset (SimCSE$_\mathrm{long}$).
+(2) Transformers specified for long sequences include Longformer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT}.
+We train two versions of \our~with BERT and Longformer (i.e.,~\our$_\mathrm{bert}$ and \our$_{\mathrm{long}}$) for comparison.
+We do not include RoBERTa~\cite{Liu2019RoBERTaAR}, IS-BERT~\cite{Zhang2020AnUS} and GTR~\cite{Ni2021LargeDE} as our baselines because SimCSE and INSTRUCTOR achieve better results than these methods according to their papers.
+
+\subsection{Text Classification}
+In the standard text classification task, we classify text embeddings with the full training set. 
+Training details are in Appendix~\ref{app:details}.
+
+\textbf{Datasets.}
 We use the following classic documents datasets to evaluate our method:
@@
 (5) BBCNews~\footnote{http://mlg.ucd.ie/datasets/bbc.html}.
-We do not use semantic textual similarity (STS) tasks~\cite{Agirre2012SemEval2012T6} because the sentences in these tasks are short which is not suitable to evaluate long text embeddings.
-
-\subsection{Baselines}
-We compare our pre-trained model to the baselines of two groups.
-(1) BERT based models include BERT~\cite{Devlin2019BERTPO}, SimCSE~\cite{Gao2021SimCSESC}, CT-BERT~\cite{Carlsson2021SemanticRW}.
-For a fair comparison, we also train a SimCSE with our pretraining dataset (SimCSE$_\mathrm{long}$).
-(2) Transformers specified for long sequences include Longformer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT}.
-We train two versions of \our~with BERT and Longformer (i.e.,~\our$_\mathrm{bert}$ and \our$_{\mathrm{long}}$) for comparison.
-We do not include RoBERTa~\cite{Liu2019RoBERTaAR} and IS-BERT~\cite{Zhang2020AnUS} as our baselines because SimCSE achieves better results than these methods according to the paper.
-
-\subsection{Text Classification}
-In the standard text classification task, we classify text embeddings with the full training set. 
-Training details are in Appendix~\ref{app:details}.
+We do not use semantic textual similarity (STS) tasks~\cite{Agirre2012SemEval2012T6} because the sentences in these tasks are short which is not suitable to evaluate large document embeddings.
 
@@
 Table~\ref{results} shows the evaluation results on different datasets. 
-Overall, we can see that \our~achieves the best performance over the 5 document datasets and consistently improves the document embeddings with BERT and Longformer structures. 
-Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE) outperform general language representations (i.e., BERT) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings.
-SimCSE pretrained with our document data (i.e.,~SimCSE$_{\mathrm{long}}$) has similar results as the original SimCSE which indicates simplely increasing the length of pretraining text cannot improve document embeddings.
-Compared to SimCSE and Longformer, our model achieves $3.9\%$ and $9.4\%$ average macro-F1 improvements with BERT and Longformer structures respectively.
+Overall, we can see that \our~achieves the best performance over the 4 document datasets (except INSTRUCTOR on 20News due to its data leakage) and consistently improves the document embeddings with BERT and Longformer structures.
+Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE, Contriever and INSTRUCTOR) outperform general language representations (i.e., BERT and LongFormer) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings.
+SimCSE pretrained with our document data (i.e.,~SimCSE$_{\mathrm{long}}$) has similar results as the original SimCSE which indicates simply increasing the length of pretraining text cannot improve document embeddings.
+Under the same model structures, our model achieves $3.9\%$ and $9.4\%$ average macro-F1 improvements with BERT and Longformer structures respectively compared to SimCSE and Longformer. 
+Compared to the state-of-the-art model INSTRUCTOR, our model (\our$_{\mathrm{bert}}$) can achieve $3.4\%$ improvements.
 Hence, our contrastive learning method is effective for document embeddings.
@@
 Table~\ref{results} shows the results of few-shot text classification on these five datasets. 
-We can see that \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively.
+We can see that, under the same model structure, \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively.
+Surprisingly, INSTRUCTOR achieves low performance on the NYT and BBCNews under few-shot settings.
+%and achieves 0.028+0.082+2.03+0.769. 
 These improvements are higher than standard text classification. 
-Besides, we also compare the performance of different baselines and \our$_{\mathrm{bert}}$ with different numbers of training instances on 20News. 
+Besides, we also compare the performance of different baselines (using BERT as a backbone) and \our$_{\mathrm{bert}}$ with different numbers of training instances on 20News. 
 The results in Figure~\ref{few_shot} show the improvements from our method become larger as the number of training instances decreases indicating the importance of high-quality document embeddings for low-resource settings.
@@
 \subsection{Document Retrieval}
-We use document retrieval to evaluate the ability of learning the similarity score between two vectors \cite{ Guo2016ADR}.
-We follow the document retrieval experiment \cite{Tay2020LongRA} and use the ACL Anthology Network (AAN) \cite{Radev2009TheAA} dataset, which identifies if two papers have a citation link, a common setup used in long-form document matching \cite{Jiang2019SemanticTM,Yang2020Beyond5T}.
+We conduct document retrieval to evaluate the ability to learn the similarity score between two vectors~\cite{Guo2016ADR} of documents.
+We follow the document retrieval experiment~\cite{Tay2020LongRA} and use the ACL Anthology Network (AAN)~\cite{Radev2009TheAA} dataset, which identifies if two papers have a citation link, a common setup used in long-form document matching~\cite{Jiang2019SemanticTM,Yang2020Beyond5T}.
+Specifically, for all baselines, we use models to obtain document embeddings and finetune an MLP layer on two concatenated embeddings to predict if two documents have a citation link.
 
@@
 \end{table*}
-Table~\ref{retrieval} shows the results of document retrieval experiment on AAN dataset.
+Table~\ref{retrieval} shows the results of the document retrieval experiment on AAN dataset.
+We can find that our method achieves the best results due to the effectiveness of our pretraining methods based on document splitting.
 
@@
 \label{sec:conclusion}
-In this work, we propose an unsupervised contrastive learning framework for long text embeddings. 
-Our method provides a new method for long text data augmentation without any supervision and language models can get large-scale pretraining on any long text. 
-We conduct extensive experiments on text classification tasks under fully supervised and few-shot settings.
+In this work, we propose an unsupervised contrastive learning framework for large document embeddings. 
+Our paper provides a new method for large document data augmentation without any supervision and language models can get large-scale pretraining on any large documents. 
+We conduct extensive experiments on text classification tasks under fully supervised and few-shot settings and a document retrieval task for further evaluation.
 Results show that our pre-trained model greatly outperforms state-of-the-art text embeddings, especially when the training data is limited.
@@
 Contriever~\cite{Izacard2021UnsupervisedDI} learns text embeddings for information retrieval via contrastive learning considering multilingual corpus.
-Instructor~\cite{Su2022OneEA} collects a massive dataset from 330 diverse NLP tasks and formulates all tasks into information retrieval tasks with prompts.
+INSTRUCTOR~\cite{Su2022OneEA} collects a massive dataset from 330 diverse NLP tasks and formulates all tasks into information retrieval tasks with prompts.
 Previous works either rely on massive manually annotated data~\cite{Su2022OneEA, Reimers2019SentenceBERTSE} or focus only on short text (i.e.,~sentences) embeddings~\cite{Gao2021SimCSESC}.
@@
 
-\subsection{Attention Weights}
-\label{app:attention}
-To explore the difference between \our~and other models, we analyze the attention weights of Transformers in different models on the NYT dataset (details in Appendix~\ref{app:attention}).
+% \subsection{Attention Weights}
+% \label{app:attention}
+% To explore the difference between \our~and other models, we analyze the attention weights of Transformers in different models on the NYT dataset (details in Appendix~\ref{app:attention}).
 The average weights of different kinds of words are shown in Figure~\ref{attentions}.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.8\linewidth]{fig/attentions.pdf}
-\caption{Attention weights from different models on the NYT dataset.}  
-\label{attentions}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.8\linewidth]{fig/attentions.pdf}
+% \caption{Attention weights from different models on the NYT dataset.}  
+% \label{attentions}
+% \end{figure}
 
-We compute the attention weights for Transformers as follows:
-(1) we first extract the attention weights between \texttt{[CLS]} token and all the other tokens;
-(2) we compute the averaged weights along different heads in multi-head attention;
-(3) the attention weights of the last layer in Transformers are used as the weights for words.
-Averaged values are computed for nouns, verbs, adjectives, and other words.
+% We compute the attention weights for Transformers as follows:
+% (1) we first extract the attention weights between \texttt{[CLS]} token and all the other tokens;
+% (2) we compute the averaged weights along different heads in multi-head attention;
+% (3) the attention weights of the last layer in Transformers are used as the weights for words.
+% Averaged values are computed for nouns, verbs, adjectives, and other words.
 

### 2023-06-21 emnlp2023-latex/paper.tex
changes

@@
 \newcommand{\our}{\mbox{\textsc{DocSplit}}}
+\newcommand{\ourbert}{$\our_{\mathrm{bert}}$}
+\newcommand{\ourlong}{$\our_{\mathrm{long}}$}
 % If the title and author information does not fit in the area allocated, uncomment the following
@@
 
-In this paper, we present the $\our$ which is the first unsupervised training method designed specifically for documents.
+In this paper, we present the $\our$ which is the first unsupervised pretraining method designed specifically for large documents.
 The training procedure of $\our$ can work with any model architecture to improve document representations. 
@@
 \label{sec:experiments}
-In this section, we evaluate the effectiveness of our method by conducting text classification tasks. 
-To eliminate the influence of different model structures and focus on the quality of text embeddings. 
-We freeze the parameters of different text encoders and fine-tune only a multi-layer perceptron (MLP) to classify the embeddings of text encoders.
-We also visualize the attention weights between baselines and \our.
 
-\begin{table}[t]
-\centering
-    \input{fig/dataset}
-    \caption{Statistics of datasets. Ave. and Med. stand for the average and median number of words respectively in one data instance.}
-    \label{dataset}
-\end{table}
+We perform a careful ablation study to isolate the effects of the $\our$ pretraining method on downstream task performance.
+First, we generate two different sets of baseline models: one for models using the contrastive loss, and one for models designed for large document embeddings.
+We pretrain separate models for each group of baselines.
+Then, we perform downstream experiments on standard classification, few-shot learning, and information retrieval tasks.
+In all cases, models pretrained with $\our$ outperform models pretrained with other methods.
 
+%We first describe how we pretrain our model.
+%Then we describe our classification, few-shot learning, and information retrieval evaluation tasks.
+
+%We use a standard experimental setup to evaluate the effectiveness of \our.
+%First, we pretr
+%
+%We evaluate the effectiveness of \our~using a standard procedureby pretraining two models on English language wikipedia.
+%Then we finetune the model
+%
+%In this section, we evaluate the effectiveness of our method by conducting text classification tasks. 
+%To eliminate the influence of different model structures and focus on the quality of text embeddings. 
+%We freeze the parameters of different text encoders and fine-tune only a multi-layer perceptron (MLP) to classify the embeddings of text encoders.
+%We also visualize the attention weights between baselines and \our.
+%
+%We do not use semantic textual similarity (STS) tasks~\cite{Agirre2012SemEval2012T6} because the sentences in these tasks are short which is not suitable to evaluate large document embeddings.
 \begin{table*}
@@
     % }}
-    \caption{For all performance measures, larger numbers are better.
-Our pre-trained model achieves the best results in all cases.
-*INSTRUCTOR~\cite{Su2022OneEA} includes 20News in their pretraining datasets which causes data leakage in our experiments, hence INSTRUCTOR results on 20News are not comparable to others.}
+    \caption{Larger numbers are better. Our pre-trained model achieves the best results in all cases.}
     \vspace{-3mm}
@@
 
+\subsection{Baselines}
+
+%In order to demonstrate that $\our$ is widely applicable,
+%we pretrain two models using two different architectures.
+
+All existing models pretrained with a contrastive loss are pretrained on the standard bert \cite{Devlin2019BERTPO} architecture.
+We therefore also pretrain a model using the bert architecture,
+and we call the resulting model \ourbert.
+The models trained with a contrastive loss that we compare \ourbert~to are SimCSE \cite{Gao2021SimCSESC}, CT-BERT~\cite{Carlsson2021SemanticRW}, Contriever~\cite{Izacard2021UnsupervisedDI} and INSTRUCTOR~\cite{Su2022OneEA}.\footnote{We do not compare to the popular RoBERTa~\cite{Liu2019RoBERTaAR}, IS-BERT~\cite{Zhang2020AnUS} and GTR~\cite{Ni2021LargeDE} models because SimCSE and INSTRUCTOR achieve better results than these methods according to their papers.}
+We will see that on all of our large document tasks, \ourbert~outperforms each of these other models.
+%Therefore, any performance differences we observe in model performance must be due to the pretraining method.
+
+We call the second model \ourlong~because it is pretrained on the LongFormer architecture \cite{Beltagy2020LongformerTL}.
+LongFormer uses a modified attention head that requires only $O(n)$ compute instead of the standard $O(n^2)$ that Bert uses,
+and so can handle larger context windows needed for large documents.
+Our \ourlong pretrained model inherits this computational advantage.
+We also compare to the BigBird~\cite{Zaheer2020BigBT} model,
+which is architecturally similar.
+
 \subsection{Pretraining Details}
-For pre-training, we start from the pretrained BERT-BASE model~\cite{Devlin2019BERTPO} and the Longformer~\cite{Beltagy2020LongformerTL} model~\footnote{The Longformer checkpoint is pretrained on long documents by MLM task and is available from Huggingface.}
-We follow previous works~\cite{Gao2021SimCSESC, Li2022UCTopicUC}: the masked language model (MLM) loss and the contrastive learning loss are used concurrently with in-batch negatives. 
-We use English Wikipedia~\footnote{https://en.wikipedia.org/} articles as pretraining data and each article is viewed as one training instance. 
+
+To pretrain both models, we follow the standard pretraining procedure for contrastive losses established by \citet{Gao2021SimCSESC} and \citet{Li2022UCTopicUC}.
+We simultaneously optimize both the masked language model (MLM) loss (with weight$=0.1$) and the contrastive loss (with temperature $\tau=0.05$).
+We use English Wikipedia articles as our pretraining dataset.
+These articles are long, and so we expect that a pretraining procedure designed for large documents will improve performance.
 The total number of training instances is 6,218,825.
-Our pretraining learning rate is 5e-5, batch size is 36 and 12 for BERT and Longformer structure respectively. Our model is optimized by AdamW~\cite{Kingma2014AdamAM} in 1 epoch. 
-The temperature $\tau$ in the contrastive loss is set to $0.05$ and the weight of MLM is set to $0.1$ following previous work~\cite{Gao2021SimCSESC}.
+We use AdamW \cite{Kingma2014AdamAM} with a learning rate of 5e-5.
+\ourbert uses a batch size of 36.
+And due to the larger memory requirements of the LongFormer architecture,
+\ourlong uses a batchsize of 12.
+For both models, we know that performance improvements on downstream tasks must be due to the pretraining procedure and not the dataset because all baseline models include English language wikipedia in their training set.
 
-\subsection{Baselines}
-We compare our pre-trained model to the baselines of two groups.
-(1) Language models trained for general language understanding and sentence embeddings include BERT~\cite{Devlin2019BERTPO}, SimCSE~\cite{Gao2021SimCSESC}~\footnote{SimCSE can be viewed as an ablation model without document splitting.}, CT-BERT~\cite{Carlsson2021SemanticRW}, Contriever~\cite{Izacard2021UnsupervisedDI} and INSTRUCTOR~\cite{Su2022OneEA}.
-For a fair comparison, we also train a SimCSE with our pretraining dataset (SimCSE$_\mathrm{long}$).
-(2) Transformers specified for long sequences include Longformer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT}.
-We train two versions of \our~with BERT and Longformer (i.e.,~\our$_\mathrm{bert}$ and \our$_{\mathrm{long}}$) for comparison.
-We do not include RoBERTa~\cite{Liu2019RoBERTaAR}, IS-BERT~\cite{Zhang2020AnUS} and GTR~\cite{Ni2021LargeDE} as our baselines because SimCSE and INSTRUCTOR achieve better results than these methods according to their papers.
+%\subsection{Baselines}
+%
+%We compare our two pre-trained model to baselines with similar architectures and different pretraining strategies.
+%
+%
+%For \ourbert
+%(1) Language models trained for general language understanding and sentence embeddings include BERT~\cite{Devlin2019BERTPO}, SimCSE~\cite{Gao2021SimCSESC}~\footnote{SimCSE can be viewed as an ablation model without document splitting.}, CT-BERT~\cite{Carlsson2021SemanticRW}, Contriever~\cite{Izacard2021UnsupervisedDI} and INSTRUCTOR~\cite{Su2022OneEA}.
+%For a fair comparison, we also train a SimCSE with our pretraining dataset (SimCSE$_\mathrm{long}$).
+%(2) Transformers specified for long sequences include Longformer~\cite{Beltagy2020LongformerTL} and BigBird~\cite{Zaheer2020BigBT}.
+%We train two versions of \our~with BERT and Longformer (i.e.,~\our$_\mathrm{bert}$ and \our$_{\mathrm{long}}$) for comparison.
 
@@
 (5) BBCNews~\footnote{http://mlg.ucd.ie/datasets/bbc.html}.
-We do not use semantic textual similarity (STS) tasks~\cite{Agirre2012SemEval2012T6} because the sentences in these tasks are short which is not suitable to evaluate large document embeddings.
+
+%\begin{table}[t]
+%\centering
+\input{fig/dataset}
+%\label{dataset}
+%\end{table}
 
@@
 Overall, we can see that \our~achieves the best performance over the 4 document datasets (except INSTRUCTOR on 20News due to its data leakage) and consistently improves the document embeddings with BERT and Longformer structures.
+INSTRUCTOR~\cite{Su2022OneEA} includes 20News in their pretraining datasets which causes data leakage in our experiments, hence INSTRUCTOR results on 20News are not comparable to others.
 Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE, Contriever and INSTRUCTOR) outperform general language representations (i.e., BERT and LongFormer) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings.
@@
 \begin{enumerate}[nosep,leftmargin=*]
-    \item Our method requires human-annotated data, which is expensive and time-consuming.
-    \item Our method focuses on document embeddings, we cannot claim the method works well for sentence embeddings.
-    \item Due to computing resource limitations, the text used in our work cannot be extremely long to verify the effectiveness of our method in this case.
+    %\item Our method requires human-annotated data, which is expensive and time-consuming.
+    \item Generative models cannot be trained using $\our$, but they can be trained using token masking.
+    \item We do not know how $\our$ will generalize to extremely large documents (e.g.\ book length).
+        We lack the computational resources to train models on these larger documents.
 \end{enumerate}

### 2023-06-22 emnlp2023-latex/paper.tex
lots of changes

@@
 \usepackage{latexsym}
+\usepackage{float}
 
@@
 \newcommand{\ourlong}{$\our_{\mathrm{long}}$}
+
+\newcommand{\fixme}[1]{{\color{red}{FIXME: {#1}}}}
 % If the title and author information does not fit in the area allocated, uncomment the following
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=\columnwidth]{fig/docsplit.pdf}
-\caption{Overall framework of \our.
+    %\includegraphics[width=\columnwidth]{example-image-golden.pdf}
+\caption{
+    Document splitting ($\our$) is a new pretraining strategy that uses contrastive learning.
+    The hard part of contrastive learning is generating positive instances.
+    $\our$ generates these pairs from an input data point by randomly assigning each sentence in the input document to one of the pairs.
+    %For each sentence in the input document, the sentence is randomly assigned to one of the positive instances ({\color{blue}{$T_1^+$} or \color{green}{$T_2^+$}).
+    %Overall framework of \our.
 The document is randomly divided into two exclusive subsets of sentences and the two subsets work as positive pairs for contrastive learning.
@@
 and our key contribution is a new method for generating positive samples for contrastive learning.
-To this end, we first investigate the information redundancy with two methods (details in Appendix~\ref{app:redundacy}) on five datasets for different lengths of documents.
-We find (1) information redundancy is larger as the length of the documents is increasing and (2) sentences from the same document usually contain repeated information. 
-Based on this observation, we can assume that the model can still learn the semantics of documents even if we drop some sentences.
+%To this end, we first investigate the information redundancy with two methods (details in Appendix~\ref{app:redundacy}) on five datasets for different lengths of documents.
+%We find (1) information redundancy is larger as the length of the documents is increasing and (2) sentences from the same document usually contain repeated information. 
+%Based on this observation, we can assume that the model can still learn the semantics of documents even if we drop some sentences.
 Hence, as shown in Figure~\ref{overall}, we randomly divide the original documents into two parts by sentences as positive pairs.
 Due to redundancies, our model can still recognize the two pairs have the same semantics.
-The intuition behind this method is that we expect the model will pull representations of two subsets together in the latent space by paying more attention to common keywords so that the model can learn key information from documents automatically.
+%The intuition behind this method is that we expect the model will pull representations of two subsets together in the latent space by paying more attention to common keywords so that the model can learn key information from documents automatically.
 
@@
 In this section, we first formally define contrastive learning, then we describe our \our~method.
+
+%\subsection{Overview of Contrastive Learning}
+%
+%Contrastive learning is a method for unsupervised pretraining of deep neural networks.
+%The idea was first introduced by \citet{Hadsell2006DimensionalityRB},
+%but saw a resurgence in popularity when it was used to pretrain multi-purpose vision models \cite{Chen2020ASF}.
+%It then became widely used in the natural language processing community to generate state-of-the-art pretrained models.
+%
+%%The original BERT transformer architecture \citep{Devlin2019BERTPO} was pretrained with token masking.
+%In this section we provide an intuitive, non-mathematical overview of contrastive learning.
+%Contrastive learning is a
+
 \subsection{Contrastive Learning}
@@
 where $\tau$ is a temperature hyperparameter and $\mathrm{sim}(\mathbf{h}_1, \mathbf{h}_2)$ is the cosine similarity $\frac{\mathbf{h}_1^{\top}\mathbf{h}_2}{\Vert \mathbf{h}_1 \Vert \cdot \Vert \mathbf{h}_2 \Vert}$.
-In this work, we encode input texts using a pre-trained language model such as BERT~\cite{Devlin2019BERTPO}.
+
+%In this work, we encode input texts using a pre-trained language model such as BERT~\cite{Devlin2019BERTPO}.
 Following BERT, we use the first special token \texttt{[CLS]} as the representation of the input and fine-tune all the parameters using the contrastive learning objective in Equation~\ref{cl}.
 
-\subsection{DocSplit}
+For negative instances, we use in-batch instances following previous contrastive frameworks~\cite{Gao2021SimCSESC, Li2022UCTopicUC}.
 The critical problem in contrastive learning is how to construct positive pairs $(x, x^{+})$.
-In representation learning for visual tasks~\cite{Chen2020ASF}, an effective solution is to take two random transformations of the same image (e.g.,~flipping, rotation).
-Similarly, in language representations, previous works~\cite{Gao2021SimCSESC, Karpukhin2020DensePR, Meng2021COCOLMCA, Li2022UCTopicUC} apply augmentation techniques such as dropout, word deletion, reordering, and masking.
+%In representation learning for visual tasks~\cite{Chen2020ASF}, an effective solution is to take two random transformations of the same image (e.g.,~flipping, rotation).
+%Similarly, in language representations, previous works~\cite{Gao2021SimCSESC, Karpukhin2020DensePR, Meng2021COCOLMCA, Li2022UCTopicUC} apply augmentation techniques such as dropout, word deletion, reordering, and masking.
 
-In this paper, we propose a new method to construct positive instances for documents. 
-The basic idea of positive instance construction for contrastive learning is adding random noises to the original data for augmentation. 
-The augmented data should have similar representations to the original data. 
-Models trained by contrastive losses on augmented data will have an increased ability to learn important features in the data.
-To add random noises in documents, we find documents usually has higher information redundancy than sentences (Table~\ref{redundancy} in Appendix). 
-With this observation, we can have an assumption: 
-the semantics of a document will not be changed even if we drop half of the document. 
-We can construct positive pairs under this assumption easily on any text dataset without supervision.
-Specifically, for each document in the dataset, we randomly split sentences in the document into two subsets and the two sentence sets do not have intersections. 
-In the two subsets, we keep the order of sentences in the original document to form two new documents. 
-According to our assumption, the two new documents should have the same semantics and hence they are used as a positive pair in contrastive learning.
+\subsection{Document Splitting ($\our$)}
+Our main contribution is the $\our$ method to construct positive instances for documents. 
+The idea is simple to describe and implement.
+Given an input document, we first split the document into sentences.
+Then each sentence is randomly assigned to eith
 
-Consider an example (in Figure~\ref{overall}) to understand our positive instance construction process:
-Suppose we have a document $T = (s_1, s_2,\dots,s_n)$ where $s_i$ is the $i$-th sentence in document and $n$ is the number of sentences, each sentence will be sent to anchor set or positive set with the same probability ($50\%$).
-The sentences in the same set (i.e.,~anchor or positive) will be concatenated in the same order of $T$ to form one positive pair $(T^+_1, T^+_2)$ for contrastive learning. 
-Positive pairs constructed by this method will not contain the same sentence and hence prevent models from overfitting on recognizing the same sentences. 
-Instead, models are guided to learn keywords appearing in positive instances so as to improve the ability to recognize key information. 
-We split the document at sentence level instead of word level (e.g.,~word deletion for augmentation) because the word-level splitting will cause the discrepancy between pretraining and finetuning and then lead to performance decay.
+There are several intuitive reasons why we should expect $\our$
+~to generate good document pairs.
+First, we can think of each positive instance as a summary of the original document.
+Second, our splitting strategy captures global information about the document.
 
-For negative instances, we use in-batch instances following previous contrastive frameworks~\cite{Gao2021SimCSESC, Li2022UCTopicUC}.
+%The basic idea of positive instance construction for contrastive learning is adding random noises to the original data for augmentation. 
+%The augmented data should have similar representations to the original data. 
+%Models trained by contrastive losses on augmented data will have an increased ability to learn important features in the data.
+%To add random noises in documents, we find documents usually has higher information redundancy than sentences (Table~\ref{redundancy} in Appendix). 
+%With this observation, we can have an assumption: 
+%the semantics of a document will not be changed even if we drop half of the document. 
+%We can construct positive pairs under this assumption easily on any text dataset without supervision.
+%Specifically, for each document in the dataset, we randomly split sentences in the document into two subsets and the two sentence sets do not have intersections. 
+%In the two subsets, we keep the order of sentences in the original document to form two new documents. 
+%According to our assumption, the two new documents should have the same semantics and hence they are used as a positive pair in contrastive learning. 
+%
+%Consider an example (in Figure~\ref{overall}) to understand our positive instance construction process:
+%Suppose we have a document $T = (s_1, s_2,\dots,s_n)$ where $s_i$ is the $i$-th sentence in document and $n$ is the number of sentences, each sentence will be sent to anchor set or positive set with the same probability ($50\%$).
+%The sentences in the same set (i.e.,~anchor or positive) will be concatenated in the same order of $T$ to form one positive pair $(T^+_1, T^+_2)$ for contrastive learning. 
+%Positive pairs constructed by this method will not contain the same sentence and hence prevent models from overfitting on recognizing the same sentences. 
+%Instead, models are guided to learn keywords appearing in positive instances so as to improve the ability to recognize key information. 
+%We split the document at sentence level instead of word level (e.g.,~word deletion for augmentation) because the word-level splitting will cause the discrepancy between pretraining and finetuning and then lead to performance decay.
+
+\section{Related Work}
+\label{sec:related}
+
+There are two categories of related work:
+models trained using contrastive learning,
+and models designed for large documents.
+
+\subsection{Contrastive Pretraining}
+\label{sec:contrastive}
+
+Contrastive learning has shown remarkable recent success for developing sentence embeddings.
+The simplest method is SimCSE \cite{Gao2021SimCSESC},
+which uses dropout to generate correlated positive samples.
+The contrastive tension method \cite{Carlsson2021SemanticRW} is similarly generic,
+but has a much more complicated implementation involving multiple models trained jointly.
+Because both of these pretraining strategies are generic,
+they can be used with any type of input including documents;
+but they do not take explicit advantage of document structure.
+%CT-BERT \cite{Carlsson2021SemanticRW} uses a pair of training models (contrastive tension).
+The INSTRUCTOR model \cite{Su2022OneEA} is the current state-of-the-art model for most downstream tasks.
+The contrastive objective for this model requires a specially constructed corpus of manual-human annotations,
+and this corpus is limited only to sentence-level annotations instead of document-level annotations.
+We show that our model significantly improves on INSTRUCTOR on document level tasks, and it is not clear how to extend the INSTRUCTOR model to document-level tasks because human annotation for documents is significantly more expensive than for sentences.
+The Contriever model \cite{Izacard2021UnsupervisedDI} uses a contrastive objective most similar to our own.
+They use the inverse cloze and document cropping tasks for pretraining.
+In document cropping, a document is divided in half and the two halves are used as the positive samples;
+in inverse cloze, a contiguous substring of the document is used as one positive sample and all other strings are used as the negative sample.
+The $\our$ pretraining method can be seen as a generalization of these methods.
+%It is evaluated only on information retrieval setting.
+%INSTRUCTOR~\cite{Su2022OneEA} uses instruction tuning.
+%They create a manually annotated corpus of 330 different datasets.
+
+\subsection{Large Document Architectures}
+
+%In order to demonstrate that $\our$ is widely applicable,
+%we pretrain two models using two different architectures.
+
+All of the models discussed in Section \ref{sec:contrastive} above are based off of the BERT architecture \cite{Devlin2019BERTPO}.
+This architecture uses an attention mechanism that requires $O(n^2)$ memory and runtime,
+where $n$ is the size of the attention window.
+The maximum size of a document that a model can understand is limited by this window size,
+and so compute for these models scales quadratically with the length of the documents.
+
+A growing body of research focuses on developing new architectures with reduced computational requirements that enable processing larger documents.
+The LongFormer \cite{Beltagy2020LongformerTL} and BigBird \cite{Zaheer2020BigBT} models pioneered this line of research,
+and both models reduce the runtime of the attention mechanism to $O(n)$.
+%A variety of other architectures have subsequently been proposed like the Informer \cite{zhou2021informer}, Switch Transformer \cite{fedus2022switch}, Performer \cite{choromanski2020rethinking}, and LinFormer \cite{wang2020linformer}
+A variety of other architectures have subsequently been proposed \cite[e.g.][]{zhou2021informer,fedus2022switch,choromanski2020rethinking,wang2020linformer,liu2022ecoformer}.
+\citet{tay2022efficient} provide a survey of this large body of work.
+Importantly, all of this research focuses only on improving the computational aspects of model architecture,
+and none of these models use a training objective designed specifically for large documents.
+Because the $\our$~pretraining method is model agnostic,
+we can easily apply it to any of these newly proposed model architectures.
+For computational reasons, we limit our experimental comparisons in Section \ref{sec:experiments} below to the LongFormer and BigBird models since these are the two most influential model architectures designed for large documents.
+We find a large performance improvement when these models are trained with $\our$,
+and expect this performance improvement would extend to similar models as well.
+
+%We call the second model \ourlong~because it is pretrained on the LongFormer architecture \cite{Beltagy2020LongformerTL}.
+%LongFormer uses a modified attention head that requires only $O(n)$ compute instead of the standard $O(n^2)$ that Bert uses,
+%and so can handle larger context windows needed for large documents.
+%Our \ourlong pretrained model inherits this computational advantage.
+%We also compare to the BigBird~\cite{Zaheer2020BigBT} model,
+%which is architecturally similar.
 
@@
 
+%To properly evaluate our $\our$~pretraining method against the related work described in Section \ref{sec:related} above,
+%we pretrain two different models.
+%The first model \ourbert~uses the same BERT architecture that all other contrastive models of Section \ref{sec:contrastive} were trained on.
+%The second model \ourlong~uses the LongFormer architecture.
+
 We perform a careful ablation study to isolate the effects of the $\our$ pretraining method on downstream task performance.
-First, we generate two different sets of baseline models: one for models using the contrastive loss, and one for models designed for large document embeddings.
-We pretrain separate models for each group of baselines.
+First, we pretrain separate models for each group of baseline models described in Section \ref{sec:related} above.
+%In particular, the \ourbert~model is trained on the BERT architecture and allows us to directly compare the performance of all contrastively pretrained models of \ref{sec:contrastive}.
+%\footnote{We do not compare to the popular RoBERTa~\cite{Liu2019RoBERTaAR}, IS-BERT~\cite{Zhang2020AnUS} and GTR~\cite{Ni2021LargeDE} models because SimCSE and INSTRUCTOR achieve better results than these methods according to their papers.}
+%The \ourlong~model is trained on the LongFormer architecture and allows to see how better pretraining drastically improves the performance of these architectures designed specifically for large documents.
 Then, we perform downstream experiments on standard classification, few-shot learning, and information retrieval tasks.
-In all cases, models pretrained with $\our$ outperform models pretrained with other methods.
+In all cases, our pretrained models significantly outperform prior work.
 
@@
 % \setlength{\tabcolsep}{1.mm}{
-    \input{fig/result.tex}
+    \input{fig/result-simplified.tex}
     % }}
-    \caption{Larger numbers are better. Our pre-trained model achieves the best results in all cases.}
+    \caption{
+        In the text classification of Experiment 1, models pretrained with $\our$ outperform baseline models in all cases.
+        Larger numbers are better.
+    }
     \vspace{-3mm}
@@
 
-\subsection{Baselines}
+\subsection{Pretraining Details}
 
-%In order to demonstrate that $\our$ is widely applicable,
-%we pretrain two models using two different architectures.
-
-All existing models pretrained with a contrastive loss are pretrained on the standard bert \cite{Devlin2019BERTPO} architecture.
-We therefore also pretrain a model using the bert architecture,
-and we call the resulting model \ourbert.
-The models trained with a contrastive loss that we compare \ourbert~to are SimCSE \cite{Gao2021SimCSESC}, CT-BERT~\cite{Carlsson2021SemanticRW}, Contriever~\cite{Izacard2021UnsupervisedDI} and INSTRUCTOR~\cite{Su2022OneEA}.\footnote{We do not compare to the popular RoBERTa~\cite{Liu2019RoBERTaAR}, IS-BERT~\cite{Zhang2020AnUS} and GTR~\cite{Ni2021LargeDE} models because SimCSE and INSTRUCTOR achieve better results than these methods according to their papers.}
-We will see that on all of our large document tasks, \ourbert~outperforms each of these other models.
-%Therefore, any performance differences we observe in model performance must be due to the pretraining method.
-
-We call the second model \ourlong~because it is pretrained on the LongFormer architecture \cite{Beltagy2020LongformerTL}.
-LongFormer uses a modified attention head that requires only $O(n)$ compute instead of the standard $O(n^2)$ that Bert uses,
-and so can handle larger context windows needed for large documents.
-Our \ourlong pretrained model inherits this computational advantage.
-We also compare to the BigBird~\cite{Zaheer2020BigBT} model,
-which is architecturally similar.
-
-\subsection{Pretraining Details}
+We pretrain two models on two different architectures.
+All prior work using contrastive learning discussed in Section \ref{sec:contrastive} above evaluates their pretraining methods on the BERT architecture.
+To fairly compare against these methods, we pretrain our \ourbert~model also on this architecture.
+Ultimately, however, we are interested in large document performance, and so we expect that a model architecture designed specifically for large documents will improve performance.
+We therefore also pretrain the \ourlong~model on the LongFormer architecture.
+This second model will be used to evaluate against other models designed specifically for large documents.
 
@@
 
-\subsection{Text Classification}
-In the standard text classification task, we classify text embeddings with the full training set. 
-Training details are in Appendix~\ref{app:details}.
+\subsection{Experiment 1: Text Classification}
+%In the standard text classification task, we classify text embeddings with the full training set. 
+%Training details are in Appendix~\ref{app:details}.
+%
+%\textbf{Datasets.}
+We fine tune \ourbert, \ourlong, and all baseline models on five standard document datasets.
+The datasets are summarized in the table below:%
+\footnote{Citations for the datasets are:
+Fake News Corpus \url{https://github.com/several27/FakeNewsCorpus};
+arXiv articles dataset~\url{https://www.kaggle.com/datasets/Cornell-University/arxiv};
+20NewsGroups~\cite{Lang1995NewsWeederLT};
+New York Times Annotated Corpus (NYT) ~\cite{sandhaus2008new}; and
+BBCNews~\url{http://mlg.ucd.ie/datasets/bbc.html}.
+}
 
-\textbf{Datasets.}
-We use the following classic documents datasets to evaluate our method:
-(1) Fake News Corpus~\footnote{https://github.com/several27/FakeNewsCorpus};
-(2) 20NewsGroups~\cite{Lang1995NewsWeederLT};
-(3) arXiv articles dataset~\footnote{https://www.kaggle.com/datasets/Cornell-University/arxiv};
-(4) New York Times Annotated Corpus (NYT) ~\cite{sandhaus2008new}; and
-(5) BBCNews~\footnote{http://mlg.ucd.ie/datasets/bbc.html}.
+\begin{table}[H]
+\centering
+~~\input{fig/dataset}
+\label{dataset}
+\end{table}
 
-%\begin{table}[t]
-%\centering
-\input{fig/dataset}
-%\label{dataset}
-%\end{table}
+\noindent
+Notice in particular that every dataset has documents that exceed the standard context window length of the BERT model.
+For these documents, we follow the standard procedure and truncate the documents before passing them to BERT-based models.
 
-\textbf{Results.}
-Table~\ref{results} shows the evaluation results on different datasets. 
-Overall, we can see that \our~achieves the best performance over the 4 document datasets (except INSTRUCTOR on 20News due to its data leakage) and consistently improves the document embeddings with BERT and Longformer structures.
-INSTRUCTOR~\cite{Su2022OneEA} includes 20News in their pretraining datasets which causes data leakage in our experiments, hence INSTRUCTOR results on 20News are not comparable to others.
-Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE, Contriever and INSTRUCTOR) outperform general language representations (i.e., BERT and LongFormer) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings.
-SimCSE pretrained with our document data (i.e.,~SimCSE$_{\mathrm{long}}$) has similar results as the original SimCSE which indicates simply increasing the length of pretraining text cannot improve document embeddings.
-Under the same model structures, our model achieves $3.9\%$ and $9.4\%$ average macro-F1 improvements with BERT and Longformer structures respectively compared to SimCSE and Longformer. 
-Compared to the state-of-the-art model INSTRUCTOR, our model (\our$_{\mathrm{bert}}$) can achieve $3.4\%$ improvements.
-Hence, our contrastive learning method is effective for document embeddings.
+%\textbf{Results.}
+Table~\ref{results} shows the accuracy and F1 score of every model on these datasets.
+Notice that \ourbert~out performs all BERT-based models discussed in Section \ref{sec:contrastive},
+and \ourlong~outperforms all models on every dataset.
+There are no results for the INSTRUCTOR model on the 20News dataset because INSTRUCTOR was pretrained on this dataset and the authors state that evaluating INSTRUCTOR on datasets it was pretrained is incorrect due to data contamination.
+%Overall, we can see that \our~achieves the best performance over the 4 document datasets (except INSTRUCTOR on 20News due to its data leakage) and consistently improves the document embeddings with BERT and Longformer structures.
+%INSTRUCTOR~\cite{Su2022OneEA} includes 20News in their pretraining datasets which causes data leakage in our experiments, hence INSTRUCTOR results on 20News are not comparable to others.
+%Specifically, methods pretrained with contrastive objectives (i.e.,~CT-BERT, SimCSE, Contriever and INSTRUCTOR) outperform general language representations (i.e., BERT and LongFormer) which indicates contrastive objectives designed for text embeddings can largely improve the ability of language models to produce high-quality text embeddings.
+%SimCSE pretrained with our document data (i.e.,~SimCSE$_{\mathrm{long}}$) has similar results as the original SimCSE which indicates simply increasing the length of pretraining text cannot improve document embeddings.
+%Under the same model structures, our model achieves $3.9\%$ and $9.4\%$ average macro-F1 improvements with BERT and Longformer structures respectively compared to SimCSE and Longformer. 
+%Compared to the state-of-the-art model INSTRUCTOR, our model (\our$_{\mathrm{bert}}$) can achieve $3.4\%$ improvements.
+%Hence, our contrastive learning method is effective for document embeddings.
 
-\subsection{Few-shot Text Classification}
-To show the performance of different text embeddings under low-resource settings, we evaluate our model with few-shot training instances.
-Training details are in Appendix~\ref{app:details}.
+\subsection{Experiment 2: Few-shot Learning}
+
+Next we evaluate how $\our$~pretraining performs on classification tasks with a small number of training examples.
+We follow the standard procedure of artificially limiting the number of training examples used during training,
+and evaluating on the same test set.
+Figure 2 shows the classification accuracy on the 20News dataset as we vary the size of the training set.
+We see that \ourbert~outperforms all other BERT-based models accross all sample sizes.
+
+The results on other datasets and for LongFormer-based models are similar.
+A full set of results on other datasets is available in the Appendix.
 
@@
 \includegraphics[width=0.8\linewidth]{fig/few_shot.pdf}
-\caption{Performance of different models with different numbers of instances per class under few-shot setting.}
+\caption{
+    \ourbert~outperforms all other BERT-based models in a few-shot classification task on the 20News dataset.
+    \fixme{change x-axis to ``training examples per class''; change $\our$ to \ourbert, you can export the figure in tex instead of pdf to get the latex support needed for the legend}
+}
 \label{few_shot}
@@
 
-\textbf{Results.} 
-Table~\ref{results} shows the results of few-shot text classification on these five datasets. 
-We can see that, under the same model structure, \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively.
-Surprisingly, INSTRUCTOR achieves low performance on the NYT and BBCNews under few-shot settings.
-%and achieves 0.028+0.082+2.03+0.769. 
-These improvements are higher than standard text classification. 
-Besides, we also compare the performance of different baselines (using BERT as a backbone) and \our$_{\mathrm{bert}}$ with different numbers of training instances on 20News. 
-The results in Figure~\ref{few_shot} show the improvements from our method become larger as the number of training instances decreases indicating the importance of high-quality document embeddings for low-resource settings.
-Furthermore, our method achieves the best results under different numbers of training instances.
+%\textbf{Results.} 
+%Table~\ref{results} shows the results of few-shot text classification on these five datasets. 
+%We can see that, under the same model structure, \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively.
+%Surprisingly, INSTRUCTOR achieves low performance on the NYT and BBCNews under few-shot settings.
+%%and achieves 0.028+0.082+2.03+0.769. 
+%These improvements are higher than standard text classification. 
+%Besides, we also compare the performance of different baselines (using BERT as a backbone) and \our$_{\mathrm{bert}}$ with different numbers of training instances on 20News. 
+%The results in Figure~\ref{few_shot} show the improvements from our method become larger as the number of training instances decreases indicating the importance of high-quality document embeddings for low-resource settings.
+%Furthermore, our method achieves the best results under different numbers of training instances.
 
-\subsection{Document Retrieval}
+\subsection{Experiment 3: Document Retrieval}
 We conduct document retrieval to evaluate the ability to learn the similarity score between two vectors~\cite{Guo2016ADR} of documents.
@@
 \textbf{Results.} 
-\begin{table*}
+\begin{table}
     \centering
@@
     \label{retrieval}
-\end{table*}
+\end{table}
 Table~\ref{retrieval} shows the results of the document retrieval experiment on AAN dataset.
@@
 \section*{Ethics Statement}
-We do not anticipate any major ethical concerns; learning document embedding is a fundamental problem in natural language processing.
+
+Learning embeddings is a standard problem in natural language processing.
+Our approach uses standard training datasets and training procedures.
+There are therefore no direct ethical concerns with this research.
+%We hope that our pretrained models and pretraining strategies will become widely used,
+%but we have no control over whether
+%As with all tools, however, the embeddings our model provides can be used for either good or evil.
+
+Our total compute is relatively small.
+Pretraining our \ourbert~and \ourlong~models took about 1 month each on a standard desktop system with an NVidia 2080 GPU.
+Other models use larger GPU clusters that require considerably more energy.
+The finetuning procedures run in less than 1 day on the same system.
+
+%We do not anticipate any major ethical concerns; learning document embedding is a fundamental problem in natural language processing.
 Ethical considerations seem low-risk for the specific datasets studied here because they are all published.
@@
 \section{Appendix}
-
-\subsection{Related Work}
-
-\textbf{Text Embeddings}.
-Learning text embeddings is a fundamental task in natural language processing (NLP) which can be used in information retrieval~\cite{Thakur2021BEIRAH}, text similarity~\cite{Gao2021SimCSESC}, classification~\cite{Minaee2021DeepLB}, etc.
-Existing works focus on learning general text embeddings for different applications.
-SimCSE~\cite{Gao2021SimCSESC} augment training data by Dropout~\cite{Srivastava2014DropoutAS} to construct positive data for contrastive learning.
-Sentence-BERT~\cite{Reimers2019SentenceBERTSE} employs siamese and triplet network structures to compare the labeled sentences in the natural language inference (NLI) dataset.
-Contriever~\cite{Izacard2021UnsupervisedDI} learns text embeddings for information retrieval via contrastive learning considering multilingual corpus.
-INSTRUCTOR~\cite{Su2022OneEA} collects a massive dataset from 330 diverse NLP tasks and formulates all tasks into information retrieval tasks with prompts.
-Previous works either rely on massive manually annotated data~\cite{Su2022OneEA, Reimers2019SentenceBERTSE} or focus only on short text (i.e.,~sentences) embeddings~\cite{Gao2021SimCSESC}.
-In this paper, we study unsupervised representation learning of document embeddings which usually have longer text than general sentence embeddings and this task brings new challenges for models to understand a document.
-
-\textbf{Model Structures for Documents}.
-Due to the limitations of Transformer~\cite{Vaswani2017AttentionIA} on long documents, Another line of work studies the efficient model structures which can be effective to encode documents.
-For example, Longformer~\cite{Beltagy2020LongformerTL} introduces an attention mechanism that scales linearly with sequence length, making it easy to process long documents.
-BigBird~\cite{Zaheer2020BigBT} proposes a sparse attention mechanism that reduces this quadratic dependency to linear.
-\citet{Bulatov2022RecurrentMT} combines the memory mechanism in LSTM~\cite{Hochreiter1997LongSM} with Transformer to let transformers encode extremely long sequences.
-Comparing these methods which focus on designing models for long documents, our work studies the effective training method for long documents which can be adopted to any model structures for pre-training.
-
-\subsection{Redundancy}
-\label{app:redundacy}
-\begin{table}[t]
-    \input{fig/redundancy}
-    \caption{Information redundancies for different lengths (i.e.,~word numbers) of text: (1) 0-50 (2) 51-100 (3) 101-200 (4) 201-300 (5) more than 300.}
-    \label{redundancy}
-\end{table}
-
-We evaluate the redundancy of the text by two methods: (1) counting the repeated verbs and nouns in the text; (2) comparing inner-document and inter-document sentence similarities.
-
-For (1), we first use SpaCy~\footnote{https://spacy.io/} to find verbs and nouns and get their lemmatizations.
-Intuitively, if the redundancy of a document is high, nouns and verbs will be repeated frequently to express the same topic.
-Hence, redundancies $R$ in our paper are computed as:
-\begin{equation}
-    R = \frac{N_{\mathrm{nouns, verbs}}}{D_{\mathrm{nouns, verbs}}}
-\end{equation}
-where $N_{\mathrm{nouns, verbs}}$ denotes the number of nouns and verbs in a document and $D_{\mathrm{nouns, verbs}}$ is the number of distinct nouns and verbs.
-
-For (2), we compute sentence similarities to compare inner-document and inter-document information.
-Specifically, we first split documents into sentences and encode these sentences with pre-trained SimCSE~\cite{Gao2021SimCSESC}.
-Then, we calculate cosine similarities for every two sentences in the same documents (i.e.,~inner-document) and from different documents (i.e.,~inter-document).
-Results from five datasets are shown in Table~\ref{sent_sim}.
-We can see that sentences in the same documents have higher similarities compared to sentences from different documents.
-These results show that sentences in the same documents usually contain repeated information and hence have higher redundancy (i.e.,~sentences expressing similar semantics).
-
-\label{app:sent_sim}
-\begin{table}[t]
-    \input{fig/sent_sim}
-    \caption{Inner-document and inter-document sentences similarities measured by SimCSE.}
-    \label{sent_sim}
-\end{table}
 

### 2023-06-23 emnlp2023-latex/fig/docsplit.tex
changes

\begin{tikz}
\small
\node{
Deep learning is part of a broader family 
};
\end{tikz}

### 2023-06-23 emnlp2023-latex/paper.tex
update dataset/fewshot/result
changes

@@
 \usepackage{float}
+\usepackage{tikz}
 
@@
 
+%The standard transformer model
+
 Generating high-quality text embeddings for documents is a long-standing open problem.
@@
     %\includegraphics[width=\columnwidth]{example-image-golden.pdf}
+    %\input{fig/docsplit.tex}
 \caption{
@@
 
-In this paper, we present the $\our$ which is the first unsupervised pretraining method designed specifically for large documents.
-The training procedure of $\our$ can work with any model architecture to improve document representations. 
-Specifically, $\our$ uses contrastive learning,
+This paper presents $\our$, the first unsupervised pretraining method designed specifically for large documents.
+$\our$ is simple to use,
+and it can be applied to any model architecture to improve document representations. 
+$\our$ uses contrastive learning,
 and our key contribution is a new method for generating positive samples for contrastive learning.
+Figure \ref{overall} provides a graphical illustration of the method,
+and Section \ref{sec:method} describes the implementation details and intuition.
+
+Section \ref{sec:related} describes how $\our$ improves prior work.
+We begin by demonstrating that prior work on contrastive pretraining has focused only on sentence-level representations.
+Then we show that work on model architectures designed for large documents has ignored the problem of better pretraining methods designed to work with these architectures.
+
+%Our paper is organized as follows.
+%Section \ref{sec:method} formally describes the $\our$ pretraining method.
+%Section \ref{sec:related} describes t
+%We highlight how our $\our$ method improves on related contrastive learning frameworks like \texttt{SimCSE}
+
+In Section \ref{sec:experiments}, we describe two pretrained models based on the BERT architecture (for fair comparison to other contrastive losses) and the LongFormer architecture (for optimal performance on large documents).
+We evaluate these models on standard large document classification, few shot learning, and document retrieval tasks.
+We find that models pretrained using $\our$ significantly outperform models pretrained with all other published methods.
+
+%We conclude in Section~\ref{sec:conclusion} by emphasizing that all of our models and datasets are open source.
+
 %To this end, we first investigate the information redundancy with two methods (details in Appendix~\ref{app:redundacy}) on five datasets for different lengths of documents.
@@
 
-To evaluate the quality of document embeddings, we conduct standard and few-shot text classification on five large document datasets involved in News and scientific articles.
+%To evaluate the quality of document embeddings, we conduct standard and few-shot text classification on five large document datasets involved in News and scientific articles.
 Moreover, to further validate the effectiveness of our method, we also conduct document retrieval on the AAN dataset which is designed for long document understanding evaluation.
-The experimental results show that \our~with two kinds of model structures (i.e.,~BERT and Longformer) can both achieve significant improvements compared to state-of-the-art baselines.
+%The experimental results show that \our~with two kinds of model structures (i.e.,~BERT and Longformer) can both achieve significant improvements compared to state-of-the-art baselines.
 
@@
 
-Our paper is organized as follows.
-In Section~\ref{sec:method} we formally define the contrastive learning problem and our novel $\our$ training method.
-%We highlight how our $\our$ method improves on related contrastive learning frameworks like \texttt{SimCSE}
-In Section~\ref{sec:experiments} we develop a new experimental evaluation procedure for documents.
-We conclude in Section~\ref{sec:conclusion} by emphasizing that all of our models and datasets are open source.
-
 \section{Method}
@@
 \mathbf{h}_{N-1}^{-}\}$, where $x$ and $x^{+}$ are semantically related.
-we follow the contrastive learning framework~~\cite{Chen2020ASF, Li2022UCTopicUC} and take cross-entropy as our objective function:
+We follow the contrastive learning framework~~\cite{Chen2020ASF, Li2022UCTopicUC} and take cross-entropy as our objective function:
 \begin{equation}
@@
 Given an input document, we first split the document into sentences.
-Then each sentence is randomly assigned to eith
+Then each sentence is randomly assigned to either the $x$ or $x^+$ document.
 
-There are several intuitive reasons why we should expect $\our$
-~to generate good document pairs.
-First, we can think of each positive instance as a summary of the original document.
-Second, our splitting strategy captures global information about the document.
+This document splitting procedure results in two documents that can be thought of as ``summaries'' of the original document.
+These summaries will have similar semantic content,
+and the contrastive loss will ensure that these two documents have similar embeddings.
+Notice that because there is randomness in the document splitting procedure,
+multiple passes over the same data points will result in different contrastive instance pairs being generated.
+
+%There are several intuitive reasons why we should expect $\our$
+%~to generate good document pairs.
+%First, we can think of each positive instance as a summary of the original document.
+%Second, our splitting strategy captures global information about the document.
 
@@
 We show that our model significantly improves on INSTRUCTOR on document level tasks, and it is not clear how to extend the INSTRUCTOR model to document-level tasks because human annotation for documents is significantly more expensive than for sentences.
+
 The Contriever model \cite{Izacard2021UnsupervisedDI} uses a contrastive objective most similar to our own.
-They use the inverse cloze and document cropping tasks for pretraining.
+They use the document cropping and inverse cloze tasks for pretraining.
 In document cropping, a document is divided in half and the two halves are used as the positive samples;
@@
 \section*{Limitations}
-The limitations of our method are as follows:
-\begin{enumerate}[nosep,leftmargin=*]
-    %\item Our method requires human-annotated data, which is expensive and time-consuming.
-    \item Generative models cannot be trained using $\our$, but they can be trained using token masking.
-    \item We do not know how $\our$ will generalize to extremely large documents (e.g.\ book length).
-        We lack the computational resources to train models on these larger documents.
-\end{enumerate}
+
+%Our paper has three main limitations.
+%\item Generative models cannot be trained using $\our$, but they can be trained using token masking.
+
+We identify three limitations with our work.
+
+\textbf{Limitation 1:}
+We evaluate $\our$ using only three downstream tasks (classification, few-shot learning, and document retrieval),
+but pretrained models are useful in many other tasks as well.
+For example, the LongFormer \cite{Beltagy2020LongformerTL} is evaluated also on question answering and coreference resolution.
+We did not run these experiments only due to a lack of computational resources,
+and we hope that future work will evaluate the performance of $\our$ pretraining on other downstream tasks as well.
+We note, however, that our $\our$ experiments in some ways are more extensive than other papers' experiments.
+For example, the LongFormer paper does not include any information retrieval experiments, and we do.
+Also, the Contriever model \citep{Izacard2021UnsupervisedDI} was specifically designed for pretraining models for the downstream retrieval experiment task and only evaluates on this downstream task.
+We beat the Contriever model on this task and provide the classification and few-shot experiments in addition.
+
+\textbf{Limitation 2:}
+Our models are pretrained only on English wikipedia,
+but other models are pretrained on significantly larger datasets.
+For example, the LongFormer model was pretrained on English wikipedia and on the Books \citep{zhu2015aligning}, Real News \citep{zellers2019defending}, and Stories \citep{zellers2019defending} datasets.
+We pretrained on this smaller dataset only due to our limited computational resources.
+%For example, the INSTRUCTOR model was pretrained on a diverse range of 330 datatsets.
+Results in scaling laws \citep{kaplan2020scaling} suggest that pretraining on more data would significantly improve our models' performance,
+and so our results are reported results are likely underestimating the positive effects of $\our$ pretraining.
+
+\textbf{Limitation 3:}
+Our experiments do not evaluate how well $\our$ will work on extremely large (e.g.\ book length) documents.
+Existing large document model architectures like LongFormer \cite{Beltagy2020LongformerTL} and BigBird \cite{Zaheer2020BigBT} are still not efficient enough to train models on these extremely large documents.
+More work also needs to be done on generating suitable evaluation tasks in this extreme setting to understand $\our$ performance.
 
@@
 
-Our total compute is relatively small.
-Pretraining our \ourbert~and \ourlong~models took about 1 month each on a standard desktop system with an NVidia 2080 GPU.
+Our total compute is relatively small and so we have a small environmental impact.
+Pretraining \ourbert took about 4 days on an Nvidia 2080 GPU with 11GB of RAM,
+and pretraining \ourlong took about 4 days with a \fixme{GPU}.
 Other models use larger GPU clusters that require considerably more energy.
-The finetuning procedures run in less than 1 day on the same system.
+The finetuning procedures run in less than 1 day on the same systems.
 

### 2023-06-23 emnlp2023-latex/fig/docsplit.tex
changes

@@
-\begin{tikz}
+\begin{tikzpicture}
 \small
-\node{
-Deep learning is part of a broader family 
+    \node[draw,thick,rounded corners=.05in] (doc) [label=above:original training document ($x$)]{
+\tiny
+    \parbox{2.5in}{
+    \color{blue}
+    Deep learning is part of a broader family  of machine learning methods based on artificial neural networks with representation learning.
+    \color{magenta}
+    Artificial neural networks were inspired by information processing and distributed communication nodes in biological systems.
+    \color{blue}
+    Artificial neural networks have various differences from biological brains.
+    \color{magenta}
+    Specifically, artifical neural networks tend to be static and symbolic, whereas the biological brain of most living organisms is dynamic and analog.
+    }
 };
-\end{tikz}
+\node[below=of doc,node distance=0.0in] (placeholder) {};
+    \node[draw,thick,rounded corners=.05in,left of=placeholder,node distance=0.1in,anchor=north east]  (x1) [label=above:document summary ($x_1^+$)] {
+    \tiny
+    \color{blue}
+    \parbox{1.2in}{
+    Deep learning is part of a broader family  of machine learning methods based on artificial neural networks with representation learning.
+    Artificial neural networks have various differences from biological brains.
+}};
+    \node[draw,thick,rounded corners=.05in,right of=placeholder,node distance=0.1in, anchor=north west] (x2) [label=above:document summary ($x_2^+$)]{
+    \tiny
+    \color{magenta}
+    \parbox{1.2in}{
+    Artificial neural networks were inspired by information processing and distributed communication nodes in biological systems.
+    Specifically, artifical neural networks tend to be static and symbolic, whereas the biological brain of most living organisms is dynamic and analog.
+}
+};
+
+    \node[above of=x1, node distance=0.51in] (x1a) {};
+    \node[above of=x2, node distance=0.61in] (x2a) {};
+    \draw[->,thick] (doc) -- (x1a);
+    \draw[->,thick] (doc) -- (x2a);
+\end{tikzpicture}

### 2023-06-23 emnlp2023-latex/paper.tex
changes

@@
 \usepackage{tikz}
+\usetikzlibrary{positioning}
 
@@
 architecture.
-Our experiments show that $\our$ outperforms other pretraining methods for document classification, few shot learning, and information retrieval tasks.
+Our experiments show that $\our$ outperforms other pretraining methods for document classification, few shot learning, and document retrieval tasks.
 \end{abstract}
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{fig/docsplit.pdf}
+    \centering
+    %\includegraphics[width=\columnwidth]{fig/docsplit.pdf}
     %\includegraphics[width=\columnwidth]{example-image-golden.pdf}
-    %\input{fig/docsplit.tex}
+    \input{fig/docsplit.tex}
 \caption{
-    Document splitting ($\our$) is a new pretraining strategy that uses contrastive learning.
-    The hard part of contrastive learning is generating positive instances.
-    $\our$ generates these pairs from an input data point by randomly assigning each sentence in the input document to one of the pairs.
+    In $\our$ pretraining,
+    an input document ($x$) is split into two new document summaries ($x_1^+$ and $x_2^+$) by randomly assigning each sentence to one of the new summaries.
+    These new summaries are then used as positive instances for contrastive learning,
+    which forces the model to represent these summaries with similar embeddings.
+    %$\our$ is a new pretraining strategy that uses contrastive learning.
+    %The hard part of contrastive learning is generating positive instances.
+    %$\our$ generates these pairs from an input data point by randomly assigning each sentence in the input document to one of the pairs.
     %For each sentence in the input document, the sentence is randomly assigned to one of the positive instances ({\color{blue}{$T_1^+$} or \color{green}{$T_2^+$}).
@@
 \label{sec:method}
-In this section, we first formally define contrastive learning, then we describe our \our~method.
+We first review contrastive learning at a high level, then we describe our \our~method.
 
@@
 \subsection{Contrastive Learning}
-Contrastive Learning aims to learn effective representations by pulling semantically close neighbors together and pushing apart non-neighbors in the latent space~\cite{Hadsell2006DimensionalityRB}.
-It assumes a contrastive instance $\{x, x^{+}, x_1^{-},\dots,x_{N-1}^{-}\}$ including one positive and $N-1$ negative instances and their representations $\{\mathbf{h}, \mathbf{h}^{+}, \mathbf{h}_1^{-}, \dots,
-\mathbf{h}_{N-1}^{-}\}$, where $x$ and $x^{+}$ are semantically related.
-We follow the contrastive learning framework~~\cite{Chen2020ASF, Li2022UCTopicUC} and take cross-entropy as our objective function:
-\begin{equation}
-\label{cl}
-    l = -\log \frac{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}}{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}+ \sum_{i=1}^{N-1}e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}_i^{-})/\tau}}
-\end{equation}
-where $\tau$ is a temperature hyperparameter and $\mathrm{sim}(\mathbf{h}_1, \mathbf{h}_2)$ is the cosine similarity $\frac{\mathbf{h}_1^{\top}\mathbf{h}_2}{\Vert \mathbf{h}_1 \Vert \cdot \Vert \mathbf{h}_2 \Vert}$.
-
+Contrastive Learning learns effective representations by pulling semantically close neighbors together and pushing apart non-neighbors in the latent space~\cite{Hadsell2006DimensionalityRB}.
+Each data point $x$ is converted into a contrastive instance $\{x^{+}_1, x^{+}_2, x_1^{-},\dots,x_{N}^{-}\}$ that includes two positive examples and $N$ negative examples.
+Intuitively, the positive instances should be semantically similar to each other (they will be pushed together) and the negative instances should be semantically dissimilar to the positive instances (they will be pushed away).
+%and their representations $\{\mathbf{h}, \mathbf{h}^{+}, \mathbf{h}_1^{-}, \dots,
+%\mathbf{h}_{N-1}^{-}\}$, where $x$ and $x^{+}$ are semantically related.
+Following recent influential work \cite{Chen2020ASF,Gao2021SimCSESC,Li2022UCTopicUC}, we use cross entropy as our loss function.
+As the mathematical details are technical and not relevant to our discussion,
+we do not reproduce them here.
+%We follow the contrastive learning framework~~\cite{Chen2020ASF, Li2022UCTopicUC} and take cross-entropy as our objective function:
+%\begin{equation}
+%\label{cl}
+    %l = -\log \frac{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}}{e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}^{+})/\tau}+ \sum_{i=1}^{N-1}e^{\mathrm{sim}(\mathbf{h}, \mathbf{h}_i^{-})/\tau}}
+%\end{equation}
+%where $\tau$ is a temperature hyperparameter and $\mathrm{sim}(\mathbf{h}_1, \mathbf{h}_2)$ is the cosine similarity $\frac{\mathbf{h}_1^{\top}\mathbf{h}_2}{\Vert \mathbf{h}_1 \Vert \cdot \Vert \mathbf{h}_2 \Vert}$.
+%
 %In this work, we encode input texts using a pre-trained language model such as BERT~\cite{Devlin2019BERTPO}.
@@
 
-For negative instances, we use in-batch instances following previous contrastive frameworks~\cite{Gao2021SimCSESC, Li2022UCTopicUC}.
-The critical problem in contrastive learning is how to construct positive pairs $(x, x^{+})$.
+There are many model training methods that use contrastive learning, and what differentiates these methods is how they convert the data point $x$ into the contrastive instance.
+%For our purposes, the important part of contrastive learning is how to convert the data point $x$ into the contrastive instance of positive and negative pairs.
+It is standard practice to use in-batch instances for the negative pairs,
+and so all that remains is designing a method for constructing the positive pairs $(x_1^+, x_2^+)$.
+%For negative instances, we use in-batch instances following previous contrastive frameworks~\cite{Gao2021SimCSESC, Li2022UCTopicUC}.
+%The critical problem in contrastive learning is how to construct positive pairs $(x, x^{+})$.
 %In representation learning for visual tasks~\cite{Chen2020ASF}, an effective solution is to take two random transformations of the same image (e.g.,~flipping, rotation).
@@
 \subsection{Document Splitting ($\our$)}
-Our main contribution is the $\our$ method to construct positive instances for documents. 
+Our main contribution is the $\our$ method to construct the positive pairs needed for contrastive learning.
 The idea is simple to describe and implement.
 Given an input document, we first split the document into sentences.
-Then each sentence is randomly assigned to either the $x$ or $x^+$ document.
+Then each sentence is randomly assigned to either the $x^+_1$ or $x^+_2$ document.
 
-This document splitting procedure results in two documents that can be thought of as ``summaries'' of the original document.
+This splitting procedure results in two documents that can be thought of as ``summaries'' of the original document.
 These summaries will have similar semantic content,
@@
 multiple passes over the same data points will result in different contrastive instance pairs being generated.
+This provides built-in overfitting resistance through data augmentation when multiple epochs of the training data are used.
 
@@
 %The \ourlong~model is trained on the LongFormer architecture and allows to see how better pretraining drastically improves the performance of these architectures designed specifically for large documents.
-Then, we perform downstream experiments on standard classification, few-shot learning, and information retrieval tasks.
+Then, we perform downstream experiments on standard classification, few-shot learning, and document retrieval tasks.
 In all cases, our pretrained models significantly outperform prior work.
@@
 \centering
-~~\input{fig/dataset}
+\input{fig/dataset}
 \label{dataset}
@@
 \noindent
-Notice in particular that every dataset has documents that exceed the standard context window length of the BERT model.
-For these documents, we follow the standard procedure and truncate the documents before passing them to BERT-based models.
+%Notice in particular that every dataset has documents that exceed the standard context window length of the BERT model.
+%For these documents, we follow the standard procedure and truncate the documents before passing them to BERT-based models.
 
@@
 and \ourlong~outperforms all models on every dataset.
-There are no results for the INSTRUCTOR model on the 20News dataset because INSTRUCTOR was pretrained on this dataset and the authors state that evaluating INSTRUCTOR on datasets it was pretrained is incorrect due to data contamination.
+There are no results for INSTRUCTOR on the 20News dataset because INSTRUCTOR was pretrained on 20News,
+and the authors state that evaluating INSTRUCTOR on datasets it was pretrained is incorrect due to data contamination.
 %Overall, we can see that \our~achieves the best performance over the 4 document datasets (except INSTRUCTOR on 20News due to its data leakage) and consistently improves the document embeddings with BERT and Longformer structures.
@@
     \ourbert~outperforms all other BERT-based models in a few-shot classification task on the 20News dataset.
-    \fixme{change x-axis to ``training examples per class''; change $\our$ to \ourbert, you can export the figure in tex instead of pdf to get the latex support needed for the legend}
+    %\fixme{change x-axis to ``training examples per class''; change $\our$ to \ourbert, you can export the figure in tex instead of pdf to get the latex support needed for the legend}
 }
@@
 \subsection{Experiment 3: Document Retrieval}
-We conduct document retrieval to evaluate the ability to learn the similarity score between two vectors~\cite{Guo2016ADR} of documents.
-We follow the document retrieval experiment~\cite{Tay2020LongRA} and use the ACL Anthology Network (AAN)~\cite{Radev2009TheAA} dataset, which identifies if two papers have a citation link, a common setup used in long-form document matching~\cite{Jiang2019SemanticTM,Yang2020Beyond5T}.
-Specifically, for all baselines, we use models to obtain document embeddings and finetune an MLP layer on two concatenated embeddings to predict if two documents have a citation link.
+%We conduct document retrieval to evaluate the ability to learn the similarity score between two vectors~\cite{Guo2016ADR} of documents.
+We follow the document retrieval experiment of the Long Range Arena (LRA) benchmark \citep{Tay2020LongRA},
+which uses the ACL Anthology Network (AAN) dataset \cite{Radev2009TheAA}.
+The goal of the task is to predict whether two papers have a citation link given only their embeddings, which is a common setup used in long-form document matching~\cite{Jiang2019SemanticTM,Yang2020Beyond5T}.
+This reduces to a binary classification task and accuracy is the commonly reported performance measure.
+Figure \ref{retrieval} shows the results.
+\ourbert~ outperforms all other BERT-based models, and \ourlong~ outperforms all other models.
+%Specifically, for all baselines, we use models to obtain document embeddings and finetune an MLP layer on two concatenated embeddings to predict if two documents have a citation link.
 
-\textbf{Results.} 
-\begin{table}
+%\textbf{Results.} 
+%\begin{table}
+%    \centering
+%   \input{fig/document_rerival.tex}
+%   \caption{}
+%   \vspace{-3mm}
+%   \label{retrieval}
+%\end{table}
+
+\begin{figure}
 \centering
-    \input{fig/document_rerival.tex}
-    \caption{}
-    \vspace{-3mm}
+\includegraphics[width=0.8\linewidth]{fig/retrieval_fig.pdf}
+\caption{In the standard LRA document retrieval task,
+    \ourbert~ outperforms all other BERT-based models,
+    and \ourlong~ outperforms all other models.}
 \label{retrieval}
-\end{table}
-Table~\ref{retrieval} shows the results of the document retrieval experiment on AAN dataset.
-We can find that our method achieves the best results due to the effectiveness of our pretraining methods based on document splitting.
+\end{figure}
+
+%Table~\ref{retrieval} shows the results of the document retrieval experiment on AAN dataset.
+%We can find that our method achieves the best results due to the effectiveness of our pretraining methods based on document splitting.
 
@@
 \label{sec:conclusion}
-In this work, we propose an unsupervised contrastive learning framework for large document embeddings. 
-Our paper provides a new method for large document data augmentation without any supervision and language models can get large-scale pretraining on any large documents. 
-We conduct extensive experiments on text classification tasks under fully supervised and few-shot settings and a document retrieval task for further evaluation.
-Results show that our pre-trained model greatly outperforms state-of-the-art text embeddings, especially when the training data is limited.
+$\our$ is the first unsupervised pretraining method designed explicitly for large documents.
+$\our$ can be used to pretrain any model architecture,
+and we provide code to do so at
+\begin{center}
+    \url{https://blinded_for_review}
+\end{center}
+%$\our$ outperforms other pretraining methods for document classification, few shot learning, and document retrieval tasks.
+The LongFormer-based \ourlong model provides SOTA performance on document classification, few-shot learning, and retrieval tasks.
 
@@
 We note, however, that our $\our$ experiments in some ways are more extensive than other papers' experiments.
-For example, the LongFormer paper does not include any information retrieval experiments, and we do.
+For example, the LongFormer paper does not include any document retrieval experiments, and we do.
 Also, the Contriever model \citep{Izacard2021UnsupervisedDI} was specifically designed for pretraining models for the downstream retrieval experiment task and only evaluates on this downstream task.
 We beat the Contriever model on this task and provide the classification and few-shot experiments in addition.
+
+Much of the prior work on contrastive learning evaluates on a large number of tasks as well.
+For example, INSTRUCTOR \cite{Su2022OneEA} is evaluated on 70 different downstream tasks.
+None of these tasks, however, are applicable in our setting because these tasks include datasets with only small text and not large documents.
 
@@
 Our total compute is relatively small and so we have a small environmental impact.
-Pretraining \ourbert took about 4 days on an Nvidia 2080 GPU with 11GB of RAM,
-and pretraining \ourlong took about 4 days with a \fixme{GPU}.
+Pretraining \ourbert took 4 days on an Nvidia 2080 GPU with 11GB of RAM,
+and pretraining \ourlong took 4 days with a \fixme{GPU}.
 Other models use larger GPU clusters that require considerably more energy.

### 2023-06-23 emnlp2023-latex/paper.tex
changes
update the figures

@@
 
-\title{DocSplit: Simple Contrastive Pretraining for \\ Large Document Embeddings}
+\title{$\our$: Simple Contrastive Pretraining for \\ Large Document Embeddings}
 
@@
 Pretraining \ourbert took 4 days on an Nvidia 2080 GPU with 11GB of RAM,
-and pretraining \ourlong took 4 days with a \fixme{GPU}.
+and pretraining \ourlong took 4 days with an Nvidia Quadro RTX 8000 with 48GB of RAM.
 Other models use larger GPU clusters that require considerably more energy.
@@
 
+\subsection{Few-shot Learning}
+\begin{table}
+    \centering
+    \input{fig/results-few_shot.tex}
+    \caption{Few-shot classification on five datasets. }
+    \vspace{-3mm}
+    \label{tab:few_shot}
+\end{table}
+Table~\ref{tab:few_shot} shows the results of few-shot text classification on these five datasets. 
+We can see that, under the same model structure, \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively.
+Surprisingly, INSTRUCTOR achieves low performance on the NYT and BBCNews under few-shot settings.
+These improvements are higher than standard text classification.
+
 % \subsection{Attention Weights}
